```{r}
#This script conducts a WGCNA, heatmap, GO term analysis, and bargraphs of all differentially abundant sites
```

# Significant Kme sites

```{r}
library(WGCNA)

library(dplyr)
all.kme<- read.csv("Input/All Quantified Kme sites.csv")
all.kme.sig<- all.kme%>%
  filter(p.t_mdam_mcf7 != "ns" |
           p.t_mdam_hcc != "ns" |
           p.t_mdam_mcf10 != "ns" |
           p.t_mcf7_hcc != "ns" |
           p.t_mcf7_mcf10 != "ns" |
           p.t_hcc_mcf10 != "ns")

all.kme.sig$ID<- paste0(all.kme.sig$Format3, "-", rownames(all.kme.sig))
clean_2<- all.kme.sig[,c(104,39:54)]
dim(clean_2);names(clean_2)
```

```{r}
options(stringsAsFactors=FALSE)
```
## Setting up WGCNA
```{r}

# Read in the proteomic data set		
rownames(clean_2)<- clean_2[,c(1)]
clean_2<- clean_2[,-c(1)]
# Take a quick look at what is in the data set:
dim(clean_2)
names(clean_2)
```

```{r}
datTraits<- read.csv("Input//traits.csv")
rownames(datTraits)=datTraits[,1];datTraits=datTraits[,-1]
dim(datTraits);names(datTraits)

```
## Setting Soft Treshold 
```{r}
#clean_2<- as.data.frame(t(clean_2))
# Choose a set of soft-thresholding powers
powers = c(c(1:10), seq(from = 12, to=30, by=2))
# Call the network topology analysis function
sft = pickSoftThreshold(clean_2, powerVector = powers, verbose = 5, networkType = "signed")
# Plot the results:
svg("Proteome Figure 1 Sig kme.svg",10,5)
# sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit R^2",type="n",
     main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.8,col="red")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
     xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
     main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
dev.off()
```

#WGCNA construction
```{r}
softPower = 16;
net = blockwiseModules(clean_2, power = softPower, networkType = "signed",
                       TOMType = "signed", minModuleSize = 20,
                       reassignThreshold = 0, mergeCutHeight = 0.25,
                       numericLabels = TRUE, pamRespectsDendro = FALSE,
                       saveTOMs = TRUE,
                       saveTOMFileBase = "Example-1 ProDataTOM", 
                       verbose = 3)
table(net$colors)


# open a graphics window
svg("Proteome Figure 2_sig kme.svg",12,9)
#sizeGrWindow(12, 9)
# Convert labels to colors for plotting
mergedColors = labels2colors(net$colors)
# Plot the dendrogram and the module colors underneath
plotDendroAndColors(net$dendrograms[[1]], mergedColors[net$blockGenes[[1]]],
                    "Module colors",
                    dendroLabels = FALSE, hang = 0.03,
                    addGuide = TRUE, guideHang = 0.05)
dev.off()	
```

## Module analysis
```{r}
moduleLabels = net$colors
moduleColors = labels2colors(net$colors)
MEs = net$MEs;
geneTree = net$dendrograms[[1]];

# Define numbers of genes and samples
nGenes = ncol(clean_2);
nSamples = nrow(clean_2);
# Recalculate MEs with color labels
MEs0 = moduleEigengenes(clean_2, moduleColors)$eigengenes
MEs = orderMEs(MEs0)
moduleTraitCor = cor(MEs, datTraits, use = "p");
moduleTraitPvalue = corPvalueStudent(moduleTraitCor, nSamples);


# open a graphics window
svg("Significant kme site.svg",5,6)
# sizeGrWindow(10,6)
# Will display correlations and their p-values
textMatrix =  paste(signif(moduleTraitCor, 2), "\n(",
                    signif(moduleTraitPvalue, 1), ")", sep = "");
dim(textMatrix) = dim(moduleTraitCor)
par(mar = c(6, 8.5, 3, 3));
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = moduleTraitCor,
               xLabels = names(datTraits),
               yLabels = names(MEs),
               ySymbols = names(MEs),
               colorLabels = FALSE,
               colors = blueWhiteRed(50),
               textMatrix = textMatrix,
               setStdMargins = FALSE,
               cex.text = 0.5,
               zlim = c(-1,1),
               main = paste("Module-trait relationships"))
dev.off()


```

## Eigenpeptides with modules
```{r}

# Define variable Cancer containing the Cancer column of datTrait
Cancer = as.data.frame(datTraits$Cancer);
names(Cancer) = "Cancer"
# names (colors) of the modules
modNames = substring(names(MEs), 3)

geneModuleMembership = as.data.frame(cor(clean_2, MEs, use = "p"));
MMPvalue = as.data.frame(corPvalueStudent(as.matrix(geneModuleMembership), nSamples));
names(geneModuleMembership) = paste("MM", modNames, sep="");
names(MMPvalue) = paste("p.MM", modNames, sep="");
geneTraitSignificance = as.data.frame(cor(clean_2, Cancer, use = "p"));
GSPvalue = as.data.frame(corPvalueStudent(as.matrix(geneTraitSignificance), nSamples));
names(geneTraitSignificance) = paste("GS.", names(Cancer), sep="");
names(GSPvalue) = paste("p.GS.", names(Cancer), sep="");

# Create the starting data frame
geneInfo0 = data.frame(Peptides = names(clean_2),
                       moduleColor = moduleColors,
                       geneTraitSignificance,GSPvalue)
# Order modules by their significance for Biofuel
modOrder = order(-abs(cor(MEs, Cancer, use = "p")));
# Add module membership information in the chosen order
for (mod in 1:ncol(geneModuleMembership))
{
  oldNames = names(geneInfo0)
  geneInfo0 = data.frame(geneInfo0, geneModuleMembership[, modOrder[mod]], 
                         MMPvalue[, modOrder[mod]]);
  names(geneInfo0) = c(oldNames, paste("MM.", modNames[modOrder[mod]], sep=""),
                       paste("p.MM.", modNames[modOrder[mod]], sep=""))
}

geneInfo0<- na.omit(geneInfo0)
# Order the genes in the geneInfo variable first by module color, then by geneTraitSignificance
geneOrder = order(geneInfo0$moduleColor, -abs(geneInfo0$GS.Cancer));
geneInfo = geneInfo0[geneOrder, ]
#save WGCNA results
write.csv(geneInfo, file = "Significant Kme WGCNA result_sig kme.csv", row.names = FALSE)

```


# Separating out modules for STRING and GO term analysis
 

```{r}
library(clusterProfiler)
library(org.Hs.eg.db)
library(dplyr)
library(ggplot2)
library(stringr)


all_protein<- read.csv("Input/Trigger Channel protein Summary2.csv")

```


```{r running function and analysis}

go_enrich<- function(a,x){

df<- geneInfo%>%
  filter(moduleColor == "blue")

df$Accession<- sub("-.*", "", df$Peptides)
  
gene<- df$Accession
 
genes<-mapIds(org.Hs.eg.db, gene, "ENTREZID", "UNIPROT")

print("done mapping")

genes<- na.omit(genes)

print("Ready to enrich")

#Go to enrich
genes<- genes[!duplicated(genes)]

go_enriched<- enrichGO(genes,OrgDb = "org.Hs.eg.db", ont="all", universe =protein_bc_go)
print("Enriched")
go_enriched_df<- as.data.frame(go_enriched)
a<- deparse(substitute(a))
write.csv(go_enriched_df, paste0(a, "_",x, "GO_terms.csv"))
print("Wrote file")
#Visualizing

go_enriched_dot<-dotplot(go_enriched, split="ONTOLOGY", showCategory = 5)+
  facet_grid(ONTOLOGY~., scale="free")+
  scale_fill_continuous(limits=c(0,0.05))+ 
  scale_y_discrete(labels=function(x) str_wrap(x, width=47))

 ggsave(go_enriched_dot, file= ("blue_GO_terms.eps"), device = "eps", width = 7, height = 7) 
 
ggsave(go_enriched_dot, file= paste0(a,"_",x,"GO_terms.eps"), device = "eps", width = 7, height = 7)
print("Wrote plot")


return(go_enriched_df)
}
```

```{r}

#Make protein_bc_go aka background
gene<- all_protein$Peptide
 
genes<-mapIds(org.Hs.eg.db, gene, "ENTREZID", "UNIPROT")

protein_bc_go<- as.vector(na.omit(genes))

#Significant protein

sig_turquoise<- go_enrich(sig_kme, "turquoise")
sig_grey<- go_enrich(sig_kme, "grey")
sig_blue<- go_enrich(sig_kme, "blue")
sig_brown<- go_enrich(sig_kme, "brown")


```



# Heatmap of upregulated sites
```{r}
library(org.Hs.eg.db)
library(AnnotationDbi)
library(stringr)
library(dplyr)

#Opening up WGCNA annotations

sig_kme<- all.kme%>%
  filter(p.t_mdam_mcf7 != "ns" |
           p.t_mdam_hcc != "ns" |
           p.t_mdam_mcf10 != "ns" |
           p.t_mcf7_hcc != "ns" |
           p.t_mcf7_mcf10 != "ns" |
           p.t_hcc_mcf10 != "ns")

sig_kme$ID<- paste0(sig_kme$Format3, "-", rownames(sig_kme))

sig_kme<- sig_kme[,c(39:54,75,77,79,81,20,103,104)]
sig_kme[,24:26]<- str_split_fixed(sig_kme$Format3, "-", 3)

genes<- mapIds(org.Hs.eg.db,
               sig_kme$V24,
               "SYMBOL",
               "UNIPROT")

sig_kme$genename<- genes
sig_kme$kme.gene.name<- paste0(sig_kme$genename, "-", sig_kme$V25, "-", sig_kme$V26,"-",sig_kme$type,"-",row_number(sig_kme) )
rownames(sig_kme)<- sig_kme$kme.gene.name


#WGCNA annotation

wgcna.kme<- geneInfo[,c(1:2)]
colnames(wgcna.kme)<- c("ID", "moduleColor")
wgcna.kme<- inner_join(sig_kme, wgcna.kme, by = "ID")
wgcna.kme<- wgcna.kme[,c(28:29)]
wgcna.kme.2<- as.data.frame(wgcna.kme[,-c(1)])
rownames(wgcna.kme.2)<- wgcna.kme$kme.gene.name
colnames(wgcna.kme.2)<- "Module.Colors"

#Cell annotation

cell_annotation<-data.frame(cells= rep(c("HCC1806", "MCF10A","MCF7","MDAMB231"), each = 4))

#Z-scoring

cal_z_score <- function(x){
 (x - mean(x)) / sd(x)
}

#all replciates

sig_kme_allreps<- sig_kme[,c(1:16)]
#z scored
sig_kme_allreps[]<- lapply(sig_kme_allreps, as.numeric)
sig_kme_allreps_zscore <- t(apply(sig_kme_allreps, 1, cal_z_score)) # apply (df)
sig_kme_allreps_zscore <- na.omit(sig_kme_allreps_zscore)
#log10 of abundance
sig_kme_allreps_raw_log<- log10(sig_kme_allreps)

#Cell annotation

cell_annotation<-data.frame(cells= rep(c("HCC1806", "MCF10A","MCF7","MDAMB231"), each = 4))
rownames(cell_annotation)<- colnames(sig_kme_allreps_zscore)
  
  
  
#Mean
sig_kme_mean<- sig_kme[,c(17:20)]
#z scored
sig_kme_mean[]<- lapply(sig_kme_mean, as.numeric)
sig_kme_mean_zscore <- t(apply(sig_kme_mean, 1, cal_z_score)) # apply (df)
sig_kme_mean_zscore <- na.omit(sig_kme_mean_zscore)
#log10 of abundance
sig_kme_mean_raw_log<- log10(sig_kme_mean)


```

## Without WGCNA annotation
```{r}
library(pheatmap)

#All replicates
## z score

paletteLength <- 160

myColor <- colorRampPalette(c("navy", "white", "darkred"))(paletteLength)
myBreaks <- c(seq(min(sig_kme_allreps_zscore), 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(max(sig_kme_allreps_zscore)/paletteLength, max(sig_kme_allreps_zscore), length.out=floor(paletteLength/2)))

svg("Z-score of all Significant Kme clustered without means.svg", height = 25, width = 15)

a<- pheatmap(sig_kme_allreps_zscore,
             color = myColor,
             breaks = myBreaks,
             cellwidth = 15,
             #scale= "row",
             cellheight = 10,
             fontsize_row = 6,
             main = "Z-score of the Significant Kme Normalized Peptide Abundance",
             #cutree_rows = 3,
             border_color = NA,
             show_colnames = T,
             cluster_cols = F,
             cluster_rows = F,
             legend_breaks =c(-3,-2,-1,0,1,2,3, 3.5))
             #labels_row= c("HCC1806", "MCF10A","MCF7","MDAMB231"))

dev.off()
a

myColor <- colorRampPalette(c("navy", "white", "darkred"))(paletteLength)
myBreaks <- c(seq(min(sig_kme_allreps_raw_log), 0, length.out=ceiling(paletteLength/2) + 0.05), 
              seq(max(sig_kme_allreps_raw_log)/paletteLength, max(sig_kme_allreps_raw_log), length.out=floor(paletteLength/2)))

svg( "Abundance of all Significant Kme clustered without means.svg", height = 25, width = 15)

b<- pheatmap(sig_kme_allreps_raw_log,
             color = myColor,
             breaks = myBreaks,
             cellwidth = 15,
             #scale= "row",
             cellheight = 10,
             fontsize_row = 6,
             main = "Log10 of the Abundance of Significant Kme Normalized Peptide Abundance",
             #cutree_rows = 3,
             border_color = NA,
             show_colnames = T,
             cluster_cols = T,
             cluster_rows = T)
             #legend_breaks =c(-3,-2,-1,0,1,2,3, 3.5))
             #labels_row= c("HCC1806", "MCF10A","MCF7","MDAMB231"))

dev.off()
b


myColor <- colorRampPalette(c("navy", "white", "darkred"))(paletteLength)
myBreaks <- c(seq(min(sig_kme_mean_zscore), 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(max(sig_kme_mean_zscore)/paletteLength, max(sig_kme_mean_zscore), length.out=floor(paletteLength/2)))

svg( "Z-score of all Significant Kme clustered means.svg", height = 25, width = 10)

c<- pheatmap(sig_kme_mean_zscore,
             color = myColor,
             breaks = myBreaks,
             cellwidth = 20,
             #scale= "row",
             cellheight = 10,
             fontsize_row = 6,
             main = "Z-score of Significant Kme Normalized Peptide Abundance",
             #cutree_rows = 3,
             border_color = NA,
             show_colnames = T,
             cluster_cols = T,
             cluster_rows = T,
             legend_breaks =c(-3,-2,-1,0,1,2,3, 3.5))
             #labels_row= c("HCC1806", "MCF10A","MCF7","MDAMB231"))

dev.off()
c


myColor <- colorRampPalette(c("navy", "white", "darkred"))(paletteLength)
myBreaks <- c(seq(min(sig_kme_mean_raw_log), 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(max(sig_kme_mean_raw_log)/paletteLength, max(sig_kme_mean_raw_log), length.out=floor(paletteLength/2)))

svg( "All Significant Kme clustered log 10 means.svg", height = 25, width = 10)

d<- pheatmap(sig_kme_mean_raw_log,
             color = myColor,
             breaks = myBreaks,
             cellwidth = 20,
             #scale= "row",
             cellheight = 10,
             fontsize_row = 6,
             main = "Log10 of the Significant Kme Normalized Peptide Abundance",
             #cutree_rows = 3,
             border_color = NA,
             show_colnames = T,
             cluster_cols = T,
             cluster_rows = T)
             #legend_breaks =c(-3,-2,-1,0,1,2,3, 3.5))
             #labels_row= c("HCC1806", "MCF10A","MCF7","MDAMB231"))

dev.off()
d
```

## All reps z score with WGCNA annotation

```{r}
library(pheatmap)

#All replicates
## z score

paletteLength <- 160

myColor <- colorRampPalette(c("navy", "white", "darkred"))(paletteLength)
myBreaks <- c(seq(min(sig_kme_allreps_zscore), 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(max(sig_kme_allreps_zscore)/paletteLength, max(sig_kme_allreps_zscore), length.out=floor(paletteLength/2)))
annotation_color<- list(Module.Colors=c(blue = "blue", turquoise = "turquoise", grey = "grey", brown = "brown"),
                        cells= c(HCC1806 = "#674ea7",MCF10A="#cc0000",MCF7 = "#26b3ff", MDAMB231 = "#3ca603"))

svg("Z-score of all Significant Kme clustered without means.svg", height = 25, width = 15)

a<- pheatmap(sig_kme_allreps_zscore,
             annotation_row= wgcna.kme.2,
             annotation_colors = annotation_color,
             annotation_col = cell_annotation,
             color = myColor,
             breaks = myBreaks,
             cellwidth = 15,
             #scale= "row",
             cellheight = 10,
             fontsize_row = 8,
             main = "Z-score of the Significant Kme Normalized Peptide Abundance",
             #cutree_rows = 3,
             border_color = NA,
             show_colnames = F,
             cluster_cols = T,
             cluster_rows = T,
             legend_breaks =c(-3,-2,-1,0,1,2,3, 3.5))
             #labels_row= c("HCC1806", "MCF10A","MCF7","MDAMB231"))

dev.off()
a
```


# GO Term analysis
```{r opening up datasets and combining all proteins observed}

all.kme<- read.csv("/home/cberry/Documents/BC_TMT Analysis/All Combined Kme sites/All Quantified Kme sites.csv")

sig.kme<- all.kme %>%filter(all.kme$anova_pvalue <=0.05)

bc.prot<- read.csv("/home/cberry/Documents/BC_TMT Analysis/Proteome_stats.csv")
trig.prot<- read.csv("/home/cberry/Documents/BC_TMT Analysis/Trigger Channel Data/Combined tech reps/Trigger_channel_prot_stats_combined reps.csv")
bc.prot.vector<- as.vector(bc.prot$Accession)
trig.prot.vector<- as.vector(trig.prot$Accession)
all.prot.vector<- c(bc.prot.vector, trig.prot.vector)
all.prot.vector<- all.prot.vector[!duplicated(all.prot.vector)]
#write.table(all.prot.vector, "all.proteins.quantified.txt", row.names = F, sep = "\t", quote = F
```

```{r running function and analysis}

go_enrich<- function(x){

gene<- x$Accession
 
genes<-mapIds(org.Hs.eg.db, gene, "ENTREZID", "UNIPROT")

print("done mapping")

genes<- na.omit(genes)

#genes_ID<- genes$ENTREZID

print("Ready to enrich")

return(genes)
}
```

## All Quantified Kme
```{r Kme_bc}
protein_bc_go<- mapIds(org.Hs.eg.db, all.prot.vector, "ENTREZID", "UNIPROT")
protein_bc_go<- protein_bc_go[!duplicated(protein_bc_go)]

#All Quantified Kme
kme_bc_go<- go_enrich(all.kme)
kme_bc_go<- kme_bc_go[!duplicated(kme_bc_go)]
kme_bc_go_enriched<- enrichGO(kme_bc_go,OrgDb = "org.Hs.eg.db", ont="all", universe =protein_bc_go)
kme_bc_go_enriched_dot<-dotplot(kme_bc_go_enriched, split="ONTOLOGY")+
  facet_grid(ONTOLOGY~., scale="free")+
  scale_fill_continuous(limits=c(0,0.00025))+ 
  scale_y_discrete(labels=function(x) str_wrap(x, width=47))
kme_bc_go_enriched_dot
ggsave(kme_bc_go_enriched_dot, file= "Kme_all_GO_terms.eps", device = "eps", width = 7, height = 10)
kme_bc_go_enriched_df<- as.data.frame(kme_bc_go_enriched)
write.csv(kme_bc_go_enriched_df, "Kme_all_Go_enrichment.csv")
# n = 202 proteins
#Sig Kme sites
sig_kme_go<- go_enrich(sig.kme)
sig_kme_go<- sig_kme_go[!duplicated(sig_kme_go)]
sig_kme_go_enriched<- enrichGO(sig_kme_go,OrgDb = "org.Hs.eg.db", ont="all", universe =protein_bc_go)
sig_kme_go_enriched_dot<-dotplot(sig_kme_go_enriched, split="ONTOLOGY")+
  facet_grid(ONTOLOGY~., scale="free")+
  scale_fill_continuous(limits=c(0,0.01))+ 
  scale_y_discrete(labels=function(x) str_wrap(x, width=47))
sig_kme_go_enriched_dot
ggsave(sig_kme_go_enriched_dot, file= "Sig_Kme_all_GO_terms.eps", device = "eps", width = 7, height = 10)
sig_kme_go_enriched<- as.data.frame(sig_kme_go_enriched)
write.csv(sig_kme_go_enriched, "Sig_Kme_all_Go_enrichment.csv")
# n = 99 proteins
```


# Looking at Upregulated sites
```{r}
up_mdamb<- all.kme%>%
  filter(p.t_mdam_mcf7 =="Up in MDAMB231" & 
           p.t_mdam_mcf10 == "Up in MDAMB231"&
           p.t_mdam_hcc == "Up in MDAMB231")

up_mdamb$type<- "MDAMB231"
  
up_hcc<-all.kme%>%
  filter(p.t_mdam_hcc =="Up in HCC1806"&
         p.t_mcf7_hcc =="Up in HCC1806"&
           p.t_hcc_mcf10 == "Up in HCC1806")

up_hcc$type<- "HCC1806"  

up_mcf7<-all.kme %>%
  filter(p.t_mdam_mcf7 =="Up in MCF7"&
         p.t_mcf7_hcc=="Up in MCF7"&
         p.t_mcf7_mcf10 =="Up in MCF7")

up_mcf7$type<- "MCF7"

up_mcf10a<-all.kme%>%
  filter(p.t_hcc_mcf10 =="Up in MCF10A" &
           p.t_mcf7_mcf10 =="Up in MCF10A"&
           p.t_mdam_mcf10=="Up in MCF10A")


up_mcf7_v_tnbc<- all.kme%>%
  filter(
          p.t_mdam_mcf7=="Up in MCF7"&
         p.t_mcf7_hcc=="Up in MCF7")

up_mcf7_v_tnbc$type<-"MCF7_v_TNBC" 


down_mdamb<- all.kme%>%
  filter(p.t_mdam_mcf7 =="Up in MCF7" & 
           p.t_mdam_mcf10 == "Up in MCF10A"&
           p.t_mdam_hcc == "Up in HCC1806")

down_mdamb$type<- "MDAMB231"
  
down_hcc<-all.kme%>%
  filter(p.t_mdam_hcc =="Up in MDAMB231"&
         p.t_mcf7_hcc =="Up in MCF7"&
           p.t_hcc_mcf10 == "Up in MCF10A")

down_hcc$type<- "HCC1806"  

down_mcf7<-all.kme %>%
  filter(p.t_mdam_mcf7 =="Up in MDAMB231"&
         p.t_mcf7_hcc=="Up in HCC1806"&
         p.t_mcf7_mcf10 =="Up in MCF10A")

down_mcf7$type<- "MCF7"

up_mcf7_v_tnbc<- all.kme%>%
  filter(
           p.t_mdam_mcf7=="Up in MCF7"&
           p.t_mcf7_hcc=="Up in MCF7")

up_mcf7_v_tnbc$type<-"MCF7_v_TNBC" 



df_2<- rbind(up_hcc,
             up_mdamb,
             up_mcf7,
             down_hcc,
             down_mcf7,
             up_mcf7_v_tnbc,
             down_mdamb)

```

#Bar graphs of sites

```{r}
library(reshape2)
df_3<-df_2[,c(82,38:53,101)]

df_3<- df_3[!duplicated(df_3$Format4),]
df_2_melt<- melt(df_3)

df_2_melt$cell<- gsub(".*_(.*)\\_.*","\\1", df_2_melt$variable)

```
```{r}
group.colors = c(MDAMB231 = "#3ca603", MCF7 = "#26b3ff", HCC1806 = "#674ea7", MCF10A = "#cc0000")

e1<-  ggplot(df_2_melt, aes(cell, value, fill = cell ))+
  stat_summary(geom="bar", fun = mean, position = "dodge")+
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width = 0.5)+
    labs(title = "Significantly Upregulated and Downregulated Kme Sites",
         y = "Protein Normalized Kme Peptide Abundance",
         x = "")+
  facet_wrap(~Format4, scales = "free")+
    theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
    scale_fill_manual(values = group.colors)

e1

ggsave("Combined plots.nostats.eps", e1, device = "eps", height = 12, width = 15)
```


```{r}
library(ggsimplestats)
library(rstatix)
library(ggpubr)
df_2_melt$Rep<- gsub(".*_","", df_2_melt$variable)
group.colors = c(MDAMB231 = "#3ca603", MCF7 = "#26b3ff", HCC1806 = "#674ea7", MCF10A = "#cc0000")


b.plot<- ggplot(df_2_melt, aes(x = cell, y = value, group = cell, fill = cell))+
  geom_boxplot()+
  geom_jitter(aes(shape = Rep, size = 2))+
  facet_wrap(vars(Format4), scales = "free")+
  theme_bw()+
  scale_fill_manual(values = group.colors)+
    labs(title = "Kme Sites Quantified With Trigger Channel",
         y = "Normalized Kme Peptide Abundance",
         x = "")+
  stat_tukeyHSD(step.increase = 0.1,
                vjust = -0.1)+
  scale_y_continuous(expand = expansion(mult = c(0.1,0.325)))+
  stat_compare_means(method = "anova",vjust = 5)

#b.plot
ggsave("Significant Kme sites.jitter.with.trigger.eps", b.plot,device = "eps", width = 20, height = 20)  
ggsave("Significant Kme sites.jitter.with.trigger.png", b.plot,device = "png", width = 20, height = 20)  

```

#All the Kme sites

```{r}
#library(ggsimplestats)
#library(rstatix)
#library(ggpubr)

df_3<-trig.kme.stats[,c(82,38:53)]

df_3<- df_3[!duplicated(df_3$Format4),]
df_2_melt<- melt(df_3)

df_2_melt$cell<- gsub(".*_(.*)\\_.*","\\1", df_2_melt$variable)


df_2_melt$Rep<- gsub(".*_","", df_2_melt$variable)
group.colors = c(MDAMB231 = "#3ca603", MCF7 = "#26b3ff", HCC1806 = "#674ea7", MCF10A = "#cc0000")


b.plot<- ggplot(df_2_melt, aes(x = cell, y = value, group = cell, fill = cell))+
  geom_boxplot()+
  geom_jitter(aes(shape = Rep, size = 2))+
  facet_wrap(vars(Format4), scales = "free")+
  theme_bw()+
  scale_fill_manual(values = group.colors)+
    labs(title = "Kme Sites Quantified With Trigger Channel",
         y = "Normalized Kme Peptide Abundance",
         x = "")+
  stat_tukeyHSD(step.increase = 0.1,
                vjust = -0.1)+
  scale_y_continuous(expand = expansion(mult = c(0.1,0.325)))+
  stat_compare_means(method = "anova",vjust = 1)

#b.plot
ggsave("All Kme sites.jitter.with.trigger.eps", b.plot,device = "eps", width = 40, height = 40)  
ggsave("All Kme sites.jitter.with.trigger.png", b.plot,device = "png", width = 40, height = 40)  
```

