```{r}
library(dplyr)
library(stringr)
library(ggplot2)
library(UniProt.ws)
library(reshape2)
library(ggpubr)
library(ggcorrplot)
library(org.Hs.eg.db)

dep_rna<- read.csv("Input/Expression_Public_23Q2_subsetted_meta.csv")

kmt<- read.csv("Input/KMTs_2021.csv")
kdm<- read.csv("Input/KDM_2021.csv")

kmt.vector<- as.vector(kmt$Gene.Name)
kdm.vector<- as.vector(kdm$Gene.Name)
kdm.extras<- c("HR", "KDM4E", "KDM7A","KDM8","RIOX1","RIOX2","KDM8")
kdm.vector<- append(kdm.vector,kdm.extras )

dep_rna<- dep_rna[-c(1),]
dep_rna<- as.data.frame(t(dep_rna))
dep_rna<- na.omit(dep_rna)
colnames(dep_rna)<- dep_rna[2,]
dep_rna<- dep_rna[-c(1:7),]
dep_rna$Gene.Name<- rownames(dep_rna)

rna.kmt<- dep_rna %>%
  filter(Gene.Name %in% kmt.vector)

rna.kdm<-dep_rna %>%
  filter(Gene.Name %in% kdm.vector)


trig.df<- read.csv("Input//Trigger_channel_prot_stats_combined reps.csv")
#pulling out means and Accession and genename 
trig.short<- trig.df[,c(20,22,24,26,2)]

trig.short$gene.name<-mapIds(org.Hs.eg.db, 
              trig.short$Accession, 
              "SYMBOL", 
              "UNIPROT")

trig.kmt<- trig.short%>% filter(Accession %in% kmt$Uniprot.ID)
trig.kdm<- trig.short%>% filter(Accession %in% kdm$Uniprot.ID)



```

# Pearson correlation of kmts and kdms within our trigger channel dataset
```{r}
trig.kmts.kdms<- rbind(trig.kdm, trig.kmt)
rownames(trig.kmts.kdms)<- trig.kmts.kdms$gene.name
trig.kmts.kdms<- trig.kmts.kdms[,-c(5,6)]
trig.kmts.kdms<- as.matrix(t(trig.kmts.kdms))


protein.kmt.kdm.cor<- cor(trig.kmts.kdms)
protein.kmt.kdm.cor.pval<- cor_pmat(trig.kmts.kdms)


a<-ggcorrplot(protein.kmt.kdm.cor,
           hc.order = T,
          # type = "lower",
           lab = F,
           outline.color = "grey",
           colors = c("#6D9EC1", "white", "#E46726"),
           p.mat = protein.kmt.kdm.cor.pval,
           ggtheme = ggplot2::theme_bw(),
          insig = "blank")


ggsave("trig channel kmt and kdm correlation plot without xs.svg", a, device = "svg", width = 10, height = 10)

```

# Making a scatterplot of the KDM protein and mRNA values
```{r}
library(reshape2)
library(ggplot2)
library(ggpubr)
trig.kdm.short<- trig.kdm[,c(1:3,6)]
colnames(trig.kdm.short)<- colnames(rna.kdm)
rownames(trig.kdm.short)<- paste0(trig.kdm.short$Gene.Name,"-protein")
rownames(rna.kdm)<- paste0(rna.kdm$Gene.Name, "-rna")
trig.kdm.short$type<- "Protein"
trig.kdm.short.melt<- melt(trig.kdm.short)


rna.kdm$type<- "mRNA"
rna.kdm.melt<- melt(rna.kdm, id=c("Gene.Name", "type"))

kdm_all<- left_join(trig.kdm.short.melt, rna.kdm.melt, by = c("Gene.Name", "variable"))

kdm_all$value.x<-as.numeric(as.character(kdm_all$value.x))
kdm_all$value.y<-as.numeric(as.character(kdm_all$value.y))



```

```{r}
#All together
library(RColorBrewer)
colourCount = length(unique(kdm_all$Gene.Name))
getPalette = colorRampPalette(brewer.pal(12, "Accent"))

graph<-ggplot(kdm_all, mapping =aes(x = log10(value.x), y = value.y))+
  geom_point(aes(color = Gene.Name, shape = variable, size = 5))+
  #facet_wrap(~ variable)
  theme_bw()+
  xlab("log10(Average Protein Abundance)")+
  ylab ("TPM+1")+
  geom_smooth(method = "lm", color = "black")+
  stat_cor()+
    theme(legend.position="bottom") +
  guides(fill=guide_legend(nrow=2))+
  scale_color_manual(values = getPalette(colourCount))

ggsave("KDM protein vs mrna all combined.eps", graph, device = "eps", width = 10, height = 10)

```

```{r}
  group.colors = c("MDAMB231" = "#3ca603", "MCF7" = "#26b3ff", "HCC1806" = "#674ea7")


a<-ggplot(kdm_all, mapping =aes(x = log10(value.x), y = value.y))+
  geom_point(aes(color = variable, size =5))+
  facet_wrap(~ Gene.Name, ncol = 4, scales = "free")+
  theme_bw()+
  xlab("log10(Average Protein Abundance)")+
  ylab ("TPM+1")+
  geom_smooth(method = "lm", color="black", linewidth = 0.5)+
  stat_cor(hjust=0,vjust=5.5, method = "pearson",size=3)+
  scale_color_manual(values = group.colors)

ggsave("KDM protein vs mrna separated by kdm.eps", a, device = "eps", width = 10, height = 15)
```

# Pearson Correlation between the trigger Channel and combined significant kme sites

```{r}
library(org.Hs.eg.db)
library(dplyr)
library(stringr)
library(ggpubr)
library(ggcorrplot)

kdm<- read.csv("/home/cberry/Documents/TNBC_SILAC_Analysis/Analysis/KMT and KDM/KDM_2021.csv")
kdm.vector<- as.vector(kdm$Gene.Name)

trig.df<- read.csv("/home/cberry/Documents/BC_TMT Analysis/Trigger Channel Data/Combined tech reps/Trigger_channel_prot_stats_combined reps.csv")
#pulling outmeans and Accession and genename 
trig.short<- trig.df[,c(20,22,24,26,2)]

trig.short$gene.name<-mapIds(org.Hs.eg.db, 
              trig.short$Accession, 
              "SYMBOL", 
              "UNIPROT")

trig.kdm<- trig.short%>% filter(Accession %in% kdm$Uniprot.ID)


all.kme<- read.csv("/home/cberry/Documents/BC_TMT Analysis/All Combined Kme sites/All Quantified Kme sites.csv")
all.kme$gene.name<-mapIds(org.Hs.eg.db, 
              all.kme$Accession, 
              "SYMBOL", 
              "UNIPROT")

all.kme$position<-sub(".*-K","", all.kme$Format3)
all.kme$ID<- paste0(all.kme$gene.name, "-K",all.kme$position,"-" ,rownames(all.kme) )

all.kme<- all.kme[,c(75,77,79,81,18,106)]
colnames(all.kme)<- colnames(trig.kdm)
all.kme<- all.kme%>% filter(!hcc1806_mean == 1)



trig.kdms.kme<- rbind(trig.kdm, all.kme)
rownames(trig.kdms.kme)<- trig.kdms.kme$gene.name
trig.kdms.kme<- trig.kdms.kme[,-c(5,6)]
trig.kdms.kme<- as.matrix(t(trig.kdms.kme))
trig.kdms.kme.cor<- cor(trig.kdms.kme)
trig.kdms.kmepval<- cor_pmat(trig.kdms.kme)

```

## Writing code to extract significant correlations with KDMs.
```{r}

kdm.pval<- as.data.frame(trig.kdms.kmepval[,c(1:26)])


sig_df <- data.frame()

  x<- colnames(kdm.pval)[1]
  print(x)
  df<- kdm.pval %>% filter(kdm.pval[,1] <= 0.05)
  y<- rownames(df)
  df<- as.data.frame(df[,1])
  df$Format4<- y
  names(df)<- c(x, "Kme.ID")
  sig_df<- df

 
  
for (i in 2:ncol(kdm.pval)){
 
  x<- colnames(kdm.pval)[i]
  print(x)
  df<- kdm.pval %>% filter(kdm.pval[i] <= 0.05)
  y<- rownames(df)
  df<- as.data.frame(df[,i])
  df$Format4<- y
  names(df)<- c(x, "Kme.ID")
  print(df)
  sig_df<- merge(sig_df, df, by = "Kme.ID", all = T)
  
}

# pulling out signficiant Kme site with correlation values less than 0.09
trig.kdms.kme.cor.2<- as.data.frame(trig.kdms.kme.cor)
trig.kdms.kme.cor.2$gene.id<- rownames(trig.kdms.kme.cor.2)


x<- colnames(sig_df)[2]
df.2<- as.data.frame(sig_df[2])
rownames(df.2)<- (sig_df$Kme.ID)
df.2<- na.omit(df.2)  
sig.sites<- as.vector(rownames(df.2))
kdm.cor.sites<- trig.kdms.kme.cor.2[trig.kdms.kme.cor.2$gene.id %in%sig.sites,]
kdm.cor.sites.2<- as.data.frame(cbind(kdm.cor.sites[1], kdm.cor.sites$gene.id))
rownames(kdm.cor.sites.2)<- row.names(kdm.cor.sites)
colnames(kdm.cor.sites.2)<- c(x, "Gene.id")
kdm.cor.sites.2<- kdm.cor.sites.2%>% filter(kdm.cor.sites.2[1] <0)

for (i in 3:ncol(sig_df)) {
x<- colnames(sig_df)[i]
df.2<- as.data.frame(sig_df[i])
rownames(df.2)<- (sig_df$Kme.ID)
df.2<- na.omit(df.2)  
sig.sites<- as.vector(rownames(df.2))
kdm.cor.sites<- trig.kdms.kme.cor.2[trig.kdms.kme.cor.2$gene.id %in%sig.sites,]
df.2<- as.data.frame(cbind(kdm.cor.sites[i-1], kdm.cor.sites$gene.id))
rownames(df.2)<- row.names(kdm.cor.sites)
colnames(df.2)<- c(x, "Gene.id")
df.2<- df.2%>% filter(df.2[1] < 0)
print(df.2)
kdm.cor.sites.2<- merge(kdm.cor.sites.2, df.2, by = "Gene.id", all = T)

}


```
### get sequence info. Inner join with 7-mer sequences
```{r}
kdm.cor.sites.2[c("Gene.name", "Position", "Methyl.state", "ID")]<- str_split_fixed(kdm.cor.sites.2$Gene.id, "-",4)
kdm.cor.sites.2$Position<- substring(kdm.cor.sites.2$Position, 2)
colnames(kdm.cor.sites.2)[1]<- "gene.name"

kdm.cor.sites.2<- inner_join(all.kme, kdm.cor.sites.2, by = "gene.name")

# Motif Analysis
library(UniprotR)
#version 2.4. Published in 3.2024
#Functions to extract aa sequences for Uniprot IDs

motif_analysis<- function (df){
    
    #Vector of Uniprot IDs
    
    IDs <- df[,"Accession"]
    
    #Extract aa sequences for each Uniprot ID and store in a new df 
    
    Uniprot<- GetSequences(IDs)
    
    #Add aa sequences to a new column to df of interest
    
    
  return(Uniprot)
    
}
df_aasequence<- motif_analysis(kdm.cor.sites.2)

aasequence<- as.character(df_aasequence$Sequence)


df_aasequence$Accession<- rownames(df_aasequence)

y<- df_aasequence[,c(20,15)]

kdm.cor.sites.2.motif <- inner_join(kdm.cor.sites.2,y, by = "Accession")

kdm.cor.sites.2.motif$Position<- as.numeric(as.character(kdm.cor.sites.2.motif$Position))
motif<- c()
 
    for (i in 1:nrow(kdm.cor.sites.2.motif)) {
     
      
      #index df by aa sequence and then by +/- 3 positions from methylated residue
      motif[i] <- print(str_sub(kdm.cor.sites.2.motif[i,"Sequence"], 
                                kdm.cor.sites.2.motif[i,"Position"]-3, 
                                kdm.cor.sites.2.motif[i,"Position"]+3))
      
     }
#return df with column containing 7-mer motifs
kdm.cor.sites.2.motif <- cbind(kdm.cor.sites.2.motif, motif)
char <- nchar(kdm.cor.sites.2.motif$motif)
kdm.cor.sites.2.motif[,c(39:45)]<- str_split_fixed(kdm.cor.sites.2.motif$motif, "", 7)

write.csv(kdm.cor.sites.2.motif, "KDM and Kme negative correlations with motif.csv")
```

### heat map with KDMs on one axis and Kme on the other
```{r}

library(pheatmap)

#All replicates
## z score
kdm.cor.sites.2[is.na(kdm.cor.sites.2)]<-0
rownames(kdm.cor.sites.2)<- kdm.cor.sites.2$Gene.id
kdm.cor.sites.2<- kdm.cor.sites.2[,-c(1)]

paletteLength <- 300
myColor <- colorRampPalette(c("navy", "white", "darkred"))(paletteLength)
myBreaks <- c(seq(min(kdm.cor.sites.2), 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(max(kdm.cor.sites.2)/paletteLength, max(kdm.cor.sites.2), length.out=floor(paletteLength/2)))

svg("Correlations between KDMs and Kme.svg", height = 31, width = 10)

a<- pheatmap(kdm.cor.sites.2,
             color = myColor,
             breaks = myBreaks,
             cellwidth = 15,
             #scale= "row",
             cellheight = 5,
             fontsize_row = 4,
             main = "Correlations between KDMs and Kme",
             #cutree_rows = 3,
             border_color = "grey",
             show_colnames = T,
             show_rownames = T,
             cluster_cols = T,
             cluster_rows = T,
             legend_breaks =c(-0.99,0,0.99,1))

dev.off()
a

```

### heat map with KDMs on one axis and Kme on the other only negative correlations
```{r}

library(pheatmap)

#All replicates
## z score
kdm.cor.sites.2[is.na(kdm.cor.sites.2)]<-0
rownames(kdm.cor.sites.2)<- kdm.cor.sites.2$Gene.id
kdm.cor.sites.2<- kdm.cor.sites.2[,-c(1)]

paletteLength <- 300
myColor <- colorRampPalette(c("navy", "light blue", "white"))(paletteLength)
myBreaks <- c(seq(min(kdm.cor.sites.2), 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(max(kdm.cor.sites.2)/paletteLength, max(kdm.cor.sites.2), length.out=floor(paletteLength/2)))

svg("Correlations between KDMs and Kme negative correlations.svg", height = 15, width = 10)

a<- pheatmap(kdm.cor.sites.2,
             color = myColor,
             #breaks = myBreaks,
             cellwidth = 15,
             #scale= "row",
             cellheight = 5,
             fontsize_row = 4,
             main = "Correlations between KDMs and Kme",
             #cutree_rows = 3,
             border_color = "grey",
             show_colnames = T,
             show_rownames = T,
             cluster_cols = T,
             cluster_rows = T)

dev.off()
a

```

## Pulling out values 
### Focusing on KDM1A, KDM4B, KDM3A, and KDM5C
```{r}
library(reshape2)
#x is kdm. y is KDM witin quotations
filtering<- function(x,y){

trig.kdms.kmepval<- as.data.frame(trig.kdms.kmepval)
sig<- trig.kdms.kmepval%>%filter({{x}} <= 0.05)
trig.kdms.kme.cor<- as.data.frame(trig.kdms.kme.cor)
cor<- trig.kdms.kme.cor%>% filter({{x}} < -0.9)

sig_kmesites<- as.vector(rownames(sig))
cor<- as.vector(rownames(cor))
sig_kmesites<- all.kme[all.kme$gene.name %in% sig_kmesites,]
sig_kmesites<- sig_kmesites[sig_kmesites$gene.name %in% cor,]


kdm_kme_melt<- melt(sig_kmesites)
kdm<- trig.kdm%>% filter(gene.name == y)
print(head(kdm))
kdm<- kdm[,-c(5)]
kdm<- melt(kdm)
kdm<- inner_join(kdm, kdm_kme_melt, by = "variable")
kdm<- kdm%>% mutate(cells = case_when(variable == "hcc1806_mean" ~ "HCC1806",
                                          variable == "mdam_mean" ~"MDAMB231",
                                          variable == "mcf7_mean" ~"MCF7",
                                          variable == "mcf10a_mean" ~ "MCF10A"))

return(kdm)
}
#x is output from previous function. y is KDM in quotes
plot_function<- function(x,y){
  
  group.colors = c("MDAMB231" = "#3ca603", "MCF7" = "#26b3ff", "HCC1806" = "#674ea7", "MCF10A" = "#cc0000")

kdm_plot<- ggplot(x, aes(x = value.y, y = value.x, color = cells, size = 4))+
  geom_point()+
  facet_wrap(~gene.name.y, scales = "free", ncol = 4)+
  theme_bw()+
  xlab("Normalized Kme Peptide Abundances")+
  ylab("Protein Abundance")+
  labs(title = paste0(y," and KDM Kme Site Correlations"))+
  scale_color_manual(values = group.colors)+
  geom_smooth(method = "lm", colour = "black", fill = "black", size = 0.5 ) +
  theme(axis.text = element_text(size = 6),
        axis.text.x = element_text(angle=45, vjust=1, hjust=1))

print(kdm_plot)
return(kdm_plot)

  
}


```

#Running functions
```{r}
#KDM3A
kdm3a_correlations<- filtering(KDM3A, "KDM3A")
kdm3a_plot<- plot_function(kdm3a_correlations, "KDM3A")

#KDM4B
kdm4b_correlations<- filtering(KDM4B, "KDM4B")
kdm4b_plot<- plot_function(kdm4b_correlations, "KDM4B")

#KDM5C
kdm5c_correlations<- filtering(KDM5C, "KDM5C")
kdm5c_plot<- plot_function(kdm5c_correlations, "KDM5C")

#KDM1A
kdm1a_correlations<- filtering(KDM1A, "KDM1A")
kdm1a_plot<- plot_function(kdm1a_correlations, "KDM1A")

#KDM4E
kdm4e_correlations<- filtering(KDM4E, "KDM4E")
kdm4e_plot<- plot_function(kdm4e_correlations, "KDM4E")
ggsave("kdm4e correlation plot.eps",kdm4e_plot, device = "eps",width = 12, height = 15)

#KDM3B
kdm3b_correlations<- filtering(KDM3B, "KDM3B")
kdm3b_plot<- plot_function(kdm3b_correlations, "KDM3B")
ggsave("kdm3b correlation plot.eps",kdm3b_plot, device = "eps",width = 12, height = 15)

#PHF8
phf8_correlations<- filtering(PHF8, "PHF8")
phf8_plot<- plot_function(phf8_correlations, "PHF8")
#ggsave("phf8 correlation plot.eps",phf8_plot, device = "eps",width = 12, height = 7)

```


```{r}
library(ggpubr)

figure<- ggarrange(kdm1a_plot, phf8_plot,
                   nrow = 2)

ggsave("KDM1A and PHF8 correlation plots.eps",figure, device = "eps", width = 10, height = 10)
```

