```{r}
library(dplyr)
library(ggplot2)
library(ggpubr)


trigger<- read.csv("Input/Trigger Channel protein Summary2.csv")

```

# Number of proteins and quantified proteins for filtered detected proteins w/trigger channel
```{r}
#With Trigger

## Removing proteins that are known contaminants, have a high FDR cutoff and more than 1 unique peptide
trig_clean<-trigger%>%
  filter(X..Unique.Peptides >1)

trig_clean<- trig_clean%>%
  filter(Protein.FDR.Confidence..Combined =="High")

trig_clean<- trig_clean%>%
  filter(!grepl("CONTAMINANT",Description ))

#Number of Quantified proteins

trig_clean_2<- trig_clean[complete.cases(trig_clean[,c(35:50)]),]

#Deteted: 4384
#Quantified: 4311


```

# Cleaning up trigger channel for quant level comparison

```{r}
trig_clean<-trigger%>%
  filter(X..Unique.Peptides >1)

trig_clean<- trig_clean%>%
  filter(Protein.FDR.Confidence..Combined =="High")

trig_clean<- trig_clean%>%
  filter(!grepl("CONTAMINANT",Description ))
trig_clean<- trig_clean[complete.cases(trig_clean[,c(35:50)]),]

trig_df<- trig_clean[,c(35:50)]

#Adding a pseudocount
trig_df<- trig_df +0.1

colnames(trig_df)<- c(
                    "HCC1806_Rep1",
                    "HCC1806_Rep2",
                    "HCC1806_Rep3",
                    "HCC1806_Rep4",
                    "MCF10A_Rep1",
                    "MCF10A_Rep2",
                    "MCF10A_Rep3",
                    "MCF10A_Rep4",
                    "MCF7_Rep1",
                    "MCF7_Rep2",
                    "MCF7_Rep3",
                    "MCF7_Rep4",
                    "MDAMB231_Rep1",
                    "MDAMB231_Rep2",
                    "MDAMB231_Rep3",
                    "MDAMB231_Rep4")
trig_df$Accession<- trig_clean$Accession
trig_df<- trig_df[,c(17,1:16)]
trig_df$Description<- trig_clean$Description


#HCC1806 mean and sd

trig_df$hcc1806_mean<- rowMeans(trig_df[,c(2:5)])
trig_df$hcc1806_sd<-apply(trig_df[,2:5], 1, sd)
#MCF7 mean and sd

trig_df$mcf7_mean<- rowMeans(trig_df[,c(10:13)])
trig_df$mcf7_sd<-apply(trig_df[,10:13], 1, sd)

#MDAMB231 mean and sd

trig_df$mdam_mean<- rowMeans(trig_df[,c(14:17)])
trig_df$mdam_sd<-apply(trig_df[,14:17], 1, sd)
#MCF10A mean and sd

trig_df$mcf10a_mean<- rowMeans(trig_df[,c(6:9)])
trig_df$mcf10a_sd<-apply(trig_df[,6:9], 1, sd)


#FC to MCF10A

trig_df$mcf10_fc_mdamb231<- trig_df$mdam_mean/trig_df$mcf10a_mean
trig_df$mcf10_fc_mcf7<- trig_df$mcf7_mean/trig_df$mcf10a_mean
trig_df$mcf10_fc_hcc<- trig_df$hcc1806_mean/trig_df$mcf10a_mean




```
 
# Correlation plots

```{r}
#library(GGally)

x_MCF10a<- trig_df[,c(6:9)]
x_HCC1806<- trig_df[,c(2:5)]
x_MCF7<- trig_df[,c(10:13)]
x_MDAM<- trig_df[,c(14:17)]


a
b
c
d
ggsave("GGpairs linear modeling MCF10A prot with TC.eps", a, device = "eps", height = 5, width = 5)
ggsave("GGpairs linear modeling HCC1806 prot with TC.eps", b, device = "eps", height = 5, width = 5)
ggsave("GGpairs linear modeling MCF7 prot with TC.eps", c, device = "eps", height = 5, width =5 )
ggsave("GGpairs linear modeling MDAMB231 prot with TC.eps", d, device = "eps", height = 5, width =5 )

trig_df_combine<- trig_df[,c(25,19,21,23)]

e<-ggpairs(log2(trig_df_combine),
        title = "Correlation between the replicate averages wtih TC",
        xlab = "log2(Abundance)",
        ylab = "log2(Abundance)",
        columnLabels = c("MCF10A", "HCC1806","MCF7", "MDAMB231"),
        upper = list(continuous = wrap('cor', size = 5)),
        lower=list(continuous="smooth"))+
  theme_bw()
e

ggsave("GGpairs linear modeling Subtype prot log2 with TC.eps", e, device = "eps", height = 5, width =5 )

```

## Linear Correlation between the averages of the 4 cell types 
```{r}
bc_df_combine<- bc_df[,c(41,23,29,35)]

e<-ggpairs(log2(bc_df_combine),
        title = "Correlation between the replicate averages",
        xlab = "log2(Abundance)",
        ylab = "log2(Abundance)",
        columnLabels = c("MCF10A", "HCC1806","MCF7", "MDAMB231"),
        upper = list(continuous = wrap('cor', size = 5)),
        lower=list(continuous="smooth"))+
  theme_bw()
e

ggsave("GGpairs linear modeling Subtype prot log2.eps", e, device = "eps", height = 5, width =5 )

```

 
 
# ANOVAs and Tukeys of entire spreadsheet
```{r set up df}
trig_df_2<- na.omit(trig_df)

trig_df_2<- trig_df_2[,c(1:17)]

trig_df_t<- as.data.frame(t(trig_df_2))

colnames(trig_df_t)<- trig_df_t[1,]

trig_df_t<- trig_df_t[-c(1),]

trig_df_t$type<- rownames(trig_df_t)

trig_df_t<- trig_df_t[,c(4312,1:4311)]

trig_df_t$type<- gsub("\\_.*","", trig_df_t$type)

```


# TUKEY Analysis
```{r Tukey analysis resulting in a df with all pairwise comparisons}
#start off by doing anova on first entry in order to initiate the df with the proper column titles

  anova <- aov(trig_df_t[,2] ~ type, data = trig_df_t)
  tukey <- TukeyHSD(anova)
  prot_pairwise<- as.data.frame(t(tukey$type[, "p adj"]))
  rownames(prot_pairwise)<- colnames(trig_df_t[2])

for (i in 3:ncol(trig_df_t)){
  #Pull gene name from column heading
  column <- names(trig_df_t[i])
  #Run anova on the column against the type
  anova <- aov(trig_df_t[,i] ~ type, data = trig_df_t)
  #Run the tukey on the anova
  tukey <- TukeyHSD(anova)
  #Pull out the p value for every comparison and make it in a dataframe
  y<- as.data.frame(t(tukey$type[, "p adj"]))
  #put the rowname as the gene name
  rownames(y)<- colnames(trig_df_t[i])
  #combine with pre-initiated dataframe
  prot_pairwise<- rbind(prot_pairwise,y)
  #return the df
}
```
# Creating df with FC's against each other and adding in p values and FDR adjust p values
```{r FC}
trig_df$fc_mdamb_v_mcf7<- trig_df$mdam_mean/trig_df$mcf7_mean

trig_df$fc_mdamb_v_hcc<- trig_df$mdam_mean/trig_df$hcc1806_mean

trig_df$fc_mdamb_v_mcf10<- trig_df$mdam_mean/trig_df$mcf10a_mean

trig_df$fc_mcf7_v_hcc<- trig_df$mcf7_mean/trig_df$hcc1806_mean

trig_df$fc_mcf7_v_mcf10<- trig_df$mcf7_mean/trig_df$mcf10a_mean

trig_df$fc_hcc_v_mcf10<- trig_df$hcc1806_mean/trig_df$mcf10a_mean


prot_pairwise$Accession<- rownames(prot_pairwise)

trig_df<- inner_join(trig_df, prot_pairwise, by = "Accession")
```


# Statistical significant
```{r creating mutant columns with up and down}

#truncating df to both FC columns and padj columns

trig_df<- trig_df%>%
  mutate(p.t_mdam_mcf7= case_when(fc_mdamb_v_mcf7 > 1.2& `MDAMB231-MCF7`  <=0.05 ~ "Up in MDAMB231",
                                 fc_mdamb_v_mcf7 < 0.83 & `MDAMB231-MCF7` <=0.05 ~"Up in MCF7",
                                 TRUE ~ "ns"))

trig_df<- trig_df%>%
  mutate(p.t_mdam_hcc= case_when(fc_mdamb_v_hcc > 1.2& `MDAMB231-HCC1806` <=0.05 ~ "Up in MDAMB231",
                                 fc_mdamb_v_hcc <0.83 & `MDAMB231-HCC1806` <=0.05 ~"Up in HCC1806",
                                 TRUE ~ "ns"))
trig_df<- trig_df%>%
  mutate(p.t_mdam_mcf10= case_when(fc_mdamb_v_mcf10 > 1.2& `MDAMB231-MCF10A` <=0.05 ~ "Up in MDAMB231",
                                 fc_mdamb_v_mcf10 <0.83 & `MDAMB231-MCF10A` <=0.05 ~"Up in MCF10A",
                                 TRUE ~ "ns"))
trig_df<- trig_df%>%
  mutate(p.t_mcf7_hcc= case_when(fc_mcf7_v_hcc > 1.2 & `MCF7-HCC1806` <=0.05 ~ "Up in MCF7",
                                 fc_mcf7_v_hcc <0.83 & `MCF7-HCC1806` <=0.05 ~"Up in HCC1806",
                                 TRUE ~ "ns"))
trig_df<- trig_df%>%
  mutate(p.t_mcf7_mcf10= case_when(fc_mcf7_v_mcf10 > 1.2& `MCF7-MCF10A` <=0.05 ~ "Up in MCF7",
                                 fc_mcf7_v_mcf10 <0.83 & `MCF7-MCF10A` <=0.05 ~"Up in MCF10A",
                                 TRUE ~ "ns"))
trig_df<- trig_df%>%
  mutate(p.t_hcc_mcf10= case_when(fc_hcc_v_mcf10 > 1.2& `MCF10A-HCC1806` <=0.05 ~ "Up in HCC1806",
                                 fc_hcc_v_mcf10 <0.83 & `MCF10A-HCC1806` <=0.05 ~"Up in MCF10A",
                                 TRUE ~ "ns"))

trig_df%>%
  count(p.t_mdam_mcf7)
trig_df%>%
  count(p.t_mdam_hcc)
trig_df%>%
  count(p.t_mdam_mcf10)
trig_df%>%
  count(p.t_mcf7_hcc)
trig_df%>%
  count(p.t_mcf7_mcf10)
trig_df%>%
  count(p.t_hcc_mcf10)

#Writing a csv
#write.csv(trig_df, "Trigger_channel_prot_stats_combined reps.csv")
```


