```{r opening up the files and setting up the file}
library(GGally)
library(dplyr)

bc_protein<- read.csv("Input/No bcger Channel Protein Summary.csv")
```
#Setting Up

# Number of proteins and quantified proteins for filtered detected proteins w/o bcger channel
```{r}
#With bcger

bc_clean<-bc_protein%>%
  filter(X..Unique.Peptides >1)

bc_clean<- bc_clean%>%
  filter(Protein.FDR.Confidence..Combined =="High")

bc_clean<- bc_clean%>%
  filter(!grepl("CONTAMINANT",Description ))

# Quantified
bc_protein_clean_2<- bc_protein_clean[complete.cases(bc_protein_clean[,c(35:50)]),]

# of Detected proteins:4208
# of Quantified proteins: 4139


```


#Normalizing to mcf10a rep 1 and then averaging
```{r tmt}

#Filter for proteins with high FDR, more than 1 peptide, and not a contaminent
bc_protein<-bc_protein%>%
  filter(X..Unique.Peptides >1)

bc_protein<- bc_protein%>%
  filter(Protein.FDR.Confidence..Combined =="High")

bc_protein<- bc_protein %>%
  filter(!grepl("CONTAMINANT", Description))

bc_df<- bc_protein[complete.cases(bc_protein[,c(35:50)]),]

bc_df<- bc_protein[,c(35:50)]

bc_df<- bc_df +0.1

colnames(bc_df)<- c(
                    "HCC1806_Rep1",
                    "HCC1806_Rep2",
                    "HCC1806_Rep3",
                    "HCC1806_Rep4",
                    "MCF10A_Rep1",
                    "MCF10A_Rep2",
                    "MCF10A_Rep3",
                    "MCF10A_Rep4",
                    "MCF7_Rep1",
                    "MCF7_Rep2",
                    "MCF7_Rep3",
                    "MCF7_Rep4",
                    "MDAMB231_Rep1",
                    "MDAMB231_Rep2",
                    "MDAMB231_Rep3",
                    "MDAMB231_Rep4")
bc_df$Accession<- bc_protein$Accession
bc_df<- bc_df[,c(17,1:16)]
bc_df$Description<- bc_protein$Description

#HCC1806 / MCF10A Rep 1

bc_df$norm_hcc1806_rep1<- bc_df$HCC1806_Rep1/bc_df$MCF10A_Rep1
bc_df$norm_hcc1806_rep2<- bc_df$HCC1806_Rep2/bc_df$MCF10A_Rep1
bc_df$norm_hcc1806_rep3<- bc_df$HCC1806_Rep3/bc_df$MCF10A_Rep1
bc_df$norm_hcc1806_rep4<- bc_df$HCC1806_Rep4/bc_df$MCF10A_Rep1

#HCC1806 mean and sd

bc_df$hcc1806_mean<- rowMeans(bc_df[,c(2:5)])
bc_df$hcc1806_sd<-apply(bc_df[,2:5], 1, sd)

#MCF7/ MCF10A Rep 1
bc_df$norm_mcf7_rep1<- bc_df$MCF7_Rep1/bc_df$MCF10A_Rep1
bc_df$norm_mcf7_rep2<- bc_df$MCF7_Rep2/bc_df$MCF10A_Rep1
bc_df$norm_mcf7_rep3<- bc_df$MCF7_Rep3/bc_df$MCF10A_Rep1
bc_df$norm_mcf7_rep4<- bc_df$MCF7_Rep4/bc_df$MCF10A_Rep1

#MCF7 mean and sd

bc_df$mcf7_mean<- rowMeans(bc_df[,c(10:13)])
bc_df$mcf7_sd<-apply(bc_df[,10:13], 1, sd)

#MDAMB231/ MCF10A Rep 1
bc_df$norm_mdam_rep1<- bc_df$MDAMB231_Rep1/bc_df$MCF10A_Rep1
bc_df$norm_mdam_rep2<- bc_df$MDAMB231_Rep2/bc_df$MCF10A_Rep1
bc_df$norm_mdam_rep3<- bc_df$MDAMB231_Rep3/bc_df$MCF10A_Rep1
bc_df$norm_mdam_rep4<- bc_df$MDAMB231_Rep4/bc_df$MCF10A_Rep1

#MDAMB231 mean and sd

bc_df$mdam_mean<- rowMeans(bc_df[,c(14:17)])
bc_df$mdam_sd<-apply(bc_df[,14:17], 1, sd)

#MCF10A/ MCF10A Rep 1
bc_df$norm_mcf10a_rep1<- bc_df$MCF10A_Rep1/bc_df$MCF10A_Rep1
bc_df$norm_mcf10a_rep2<- bc_df$MCF10A_Rep2/bc_df$MCF10A_Rep1
bc_df$norm_mcf10a_rep3<- bc_df$MCF10A_Rep3/bc_df$MCF10A_Rep1
bc_df$norm_mcf10a_rep4<- bc_df$MCF10A_Rep4/bc_df$MCF10A_Rep1

#MCF10A mean and sd

bc_df$mcf10a_mean<- rowMeans(bc_df[,c(6:9)])
bc_df$mcf10a_sd<-apply(bc_df[,6:9], 1, sd)


#Normalized to MCF10A averages

bc_df$hcc1806_norm<- bc_df$hcc1806_mean/bc_df$mcf10a_mean
bc_df$mcf7_norm<- bc_df$mcf7_mean/bc_df$mcf10a_mean
bc_df$mdam_norm<- bc_df$mdam_mean/bc_df$mcf10a_mean

bc_df<- na.omit(bc_df)
```


```{r linear model across biological replicates}

x_MCF10a<- bc_df[,c(6:9)]
x_HCC1806<- bc_df[,c(2:5)]
x_MCF7<- bc_df[,c(10:13)]
x_MDAM<- bc_df[,c(14:17)]

a<-ggpairs(log2(x_MCF10a),
        title = "Correlation between MCF10A Replicates with TC",
        xlab = "log2(Abundance)",
        ylab = "log2(Abundance)",
        columnLabels = c("Rep 1", "Rep2","Rep 3", "Rep 4"),
        upper = list(continuous = wrap('cor', size = 5)),
        lower=list(continuous="smooth"))+
  theme_bw()
b<-ggpairs(log2(x_HCC1806),
        title = "Correlation between HCC1806 Replicates with TC",
        xlab = "log2(Abundance)",
        ylab = "log2(Abundance)",
        columnLabels = c("Rep 1", "Rep2","Rep 3", "Rep 4"),
        upper = list(continuous = wrap('cor', size = 5)),
        lower=list(continuous="smooth"))+
  theme_bw()
c<-ggpairs(log2(x_MCF7),
        title = "Correlation between MCF7 Replicates with TC",
        xlab = "log2(Abundance)",
        ylab = "log2(Abundance)",
        columnLabels = c("Rep 1", "Rep2","Rep 3", "Rep 4"),
        upper = list(continuous = wrap('cor', size = 5)),
        lower=list(continuous="smooth"))+
  theme_bw()
d<-ggpairs(log2(x_MDAM),
        title = "Correlation between MDAMB231 Replicates with TC",
        xlab = "log2(Abundance)",
        ylab = "log2(Abundance)",
        columnLabels = c("Rep 1", "Rep2","Rep 3", "Rep 4"),
        upper = list(continuous = wrap('cor', size = 5)),
        lower=list(continuous="smooth"))+
  theme_bw()
a
b
c
d
ggsave("GGpairs linear modeling MCF10A prot.eps", a, device = "eps", height = 5, width = 5)
ggsave("GGpairs linear modeling HCC1806 prot.eps", b, device = "eps", height = 5, width = 5)
ggsave("GGpairs linear modeling MCF7 prot.eps", c, device = "eps", height = 5, width =5 )
ggsave("GGpairs linear modeling MDAMB231 prot.eps", d, device = "eps", height = 5, width =5 )


```

# Linear Correlation between the averages of the 4 cell types 
```{r}
bc_df_combine<- bc_df[,c(41,23,29,35)]

e<-ggpairs(log2(bc_df_combine),
        title = "Correlation between the replicate averages",
        xlab = "log2(Abundance)",
        ylab = "log2(Abundance)",
        columnLabels = c("MCF10A", "HCC1806","MCF7", "MDAMB231"),
        upper = list(continuous = wrap('cor', size = 5)),
        lower=list(continuous="smooth"))+
  theme_bw()
e

ggsave("GGpairs linear modeling Subtype prot log2.eps", e, device = "eps", height = 5, width =5 )

```


#ANOVAs and Tukeys
```{r set up df}
bc_df_2<- na.omit(bc_df)

bc_df_2<- bc_df_2[,c(1:17)]

#rownames(bc_df_2)<- bc_df_2[,c(1)]
#bc_df_2<- bc_df_2[,c(2:17)]+1


bc_df_t<- as.data.frame(t(bc_df_2))


colnames(bc_df_t)<- bc_df_t[1,]
bc_df_t<- bc_df_t[-c(1),]

bc_df_t$type<- rownames(bc_df_t)

bc_df_t<- bc_df_t[,c(4132,1:4131)]

bc_df_t$type<- gsub("\\_.*","", bc_df_t$type)

```


# TUKEY Analysis
```{r Tukey analysis resulting in a df with all pairwise comparisons}
#start off by doing anova on first entry in order to initiate the df with the proper column titles

  anova <- aov(bc_df_t[,2] ~ type, data = bc_df_t)
  tukey <- TukeyHSD(anova)
  prot_pairwise<- as.data.frame(t(tukey$type[, "p adj"]))
  rownames(prot_pairwise)<- colnames(bc_df_t[2])

for (i in 3:ncol(bc_df_t)){
  #Pull gene name from column heading
  column <- names(bc_df_t[i])
  #Run anova on the column against the type
  anova <- aov(bc_df_t[,i] ~ type, data = bc_df_t)
  #Run the tukey on the anova
  tukey <- TukeyHSD(anova)
  #Pull out the p value for every comparison and make it in a dataframe
  y<- as.data.frame(t(tukey$type[, "p adj"]))
  #put the rowname as the gene name
  rownames(y)<- colnames(bc_df_t[i])
  #combine with pre-initiated dataframe
  prot_pairwise<- rbind(prot_pairwise,y)
  #return the df
}
```

# ANOVA Analysis
```{r ANOVA Loop}
#Create a vector of all the anova p values to pull out proteins to do Tukey test on

n<- vector()
anova_run<- apply(bc_df_t[,2:ncol(bc_df_t)],2, function(a){

x<- aov(a~type, data = bc_df_t)
summary(x)
y<- summary(x)[[1]][["Pr(>F)"]][[1]]
n<- append(n,y)

return(n)})

bc_df_t_2<- as.data.frame(t(bc_df_t))

bc_df_t_2<- bc_df_t_2[-c(1),]

bc_df_t_2$anova_pvalue<- anova_run

```


# Creating df with FC's against each other and adding in p values and FDR adjust p values
```{r FC}
bc_df$fc_mdamb_v_mcf7<- bc_df$mdam_mean/bc_df$mcf7_mean

bc_df$fc_mdamb_v_hcc<- bc_df$mdam_mean/bc_df$hcc1806_mean

bc_df$fc_mdamb_v_mcf10<- bc_df$mdam_mean/bc_df$mcf10a_mean

bc_df$fc_mcf7_v_hcc<- bc_df$mcf7_mean/bc_df$hcc1806_mean

bc_df$fc_mcf7_v_mcf10<- bc_df$mcf7_mean/bc_df$mcf10a_mean

bc_df$fc_hcc_v_mcf10<- bc_df$hcc1806_mean/bc_df$mcf10a_mean


prot_pairwise$Accession<- rownames(prot_pairwise)

bc_df<- inner_join(bc_df, prot_pairwise, by = "Accession")
```

# Statistical significant
```{r creating mutant columns with up and down}

#truncating df to both FC columns and padj columns

bc_df<- bc_df%>%
  mutate(p.t_mdam_mcf7= case_when(fc_mdamb_v_mcf7 > 1.2& `MDAMB231-MCF7`  <=0.05 ~ "Up in MDAMB231",
                                 fc_mdamb_v_mcf7 < 0.83 & `MDAMB231-MCF7` <=0.05 ~"Up in MCF7",
                                 TRUE ~ "ns"))

bc_df<- bc_df%>%
  mutate(p.t_mdam_hcc= case_when(fc_mdamb_v_hcc > 1.2& `MDAMB231-HCC1806` <=0.05 ~ "Up in MDAMB231",
                                 fc_mdamb_v_hcc <0.83 & `MDAMB231-HCC1806` <=0.05 ~"Up in HCC1806",
                                 TRUE ~ "ns"))
bc_df<- bc_df%>%
  mutate(p.t_mdam_mcf10= case_when(fc_mdamb_v_mcf10 > 1.2& `MDAMB231-MCF10A` <=0.05 ~ "Up in MDAMB231",
                                 fc_mdamb_v_mcf10 <0.83 & `MDAMB231-MCF10A` <=0.05 ~"Up in MCF10A",
                                 TRUE ~ "ns"))
bc_df<- bc_df%>%
  mutate(p.t_mcf7_hcc= case_when(fc_mcf7_v_hcc > 1.2 & `MCF7-HCC1806` <=0.05 ~ "Up in MCF7",
                                 fc_mcf7_v_hcc <0.83 & `MCF7-HCC1806` <=0.05 ~"Up in HCC1806",
                                 TRUE ~ "ns"))
bc_df<- bc_df%>%
  mutate(p.t_mcf7_mcf10= case_when(fc_mcf7_v_mcf10 > 1.2& `MCF7-MCF10A` <=0.05 ~ "Up in MCF7",
                                 fc_mcf7_v_mcf10 <0.83 & `MCF7-MCF10A` <=0.05 ~"Up in MCF10A",
                                 TRUE ~ "ns"))
bc_df<- bc_df%>%
  mutate(p.t_hcc_mcf10= case_when(fc_hcc_v_mcf10 > 1.2& `MCF10A-HCC1806` <=0.05 ~ "Up in HCC1806",
                                 fc_hcc_v_mcf10 <0.83 & `MCF10A-HCC1806` <=0.05 ~"Up in MCF10A",
                                 TRUE ~ "ns"))

bc_df%>%
  count(p.t_mdam_mcf7)
bc_df%>%
  count(p.t_mdam_hcc)
bc_df%>%
  count(p.t_mdam_mcf10)
bc_df%>%
  count(p.t_mcf7_hcc)
bc_df%>%
  count(p.t_mcf7_mcf10)
bc_df%>%
  count(p.t_hcc_mcf10)

#Writing a csv
#write.csv(trig_df, "No Trigger_channel_prot_stats.csv")
```

