```{r}
# This script compares the proteomes and kdms psms/peptides with and without the trigger channel
```


```{r}
library(dplyr)
library(ggplot2)
library(ggpubr)
library(VennDiagram)
library(ggforce)

#Opening up Proteins summaries
bc_protein<- read.csv("Input/No Trigger Channel Protein Summary.csv")

trigger_protein<- read.csv("Input/Trigger Channel protein Summary2.csv")


#Opening up Process Proteome data
bc_df<- read.csv("Input/No Trigger_channel_prot_stats.csv")
bc_df<- bc_df[,-c(1)]

trigger_df<- read.csv("Input/Trigger_channel_prot_stats_combined reps.csv")
trigger_df<- trigger_df[,-c(1)]

kdm<- read.csv("Input/KDM_2021.csv")
kdm.vector<- as.vector(kdm$Uniprot.ID)
gene_kdm<- kdm[,c(1,4)]
colnames(gene_kdm)<- c("Accession", "Gene.Name")

```

# Proteome Comparisons
## VennDiagram of accessions of filtered and quantified KDMs

```{r Venn Diagram}
list<- list(First.Run = bc_df$Accession,
        KDM.Trigger.Channel = trig_df$Accession)

a<-venn.diagram(
  list ,
  category.names = c("Without Trigger" , "With Trigger" ),
  filename = 'venn_Trigger.png',
  output = TRUE ,
          imagetype="png" ,
          height = 3200 , 
           width = 3200 , 
          resolution = 600,           
          compression = "lzw",
          lwd = 1,
          col=c("#000000", '#07526e'),
          fill = c(alpha("#000000",0.5), alpha('#07526e',0.5)),
          cex = 1.5,
          fontfamily = "sans",
          cat.cex = 1.20,
          cat.default.pos = "outer",
          cat.pos = c(-15, 15),
          cat.dist = c(0.045, 0.045),
          cat.fontfamily = "sans",
          cat.col = c("#000000", '#07526e'),
  scaled=T
        )

a
```


## Ggplot correlations
### Proteome Abundances
```{r Ggplot correlaitons}

big<- inner_join(trigger_df, bc_df, by = "Accession")

big<- big%>%
  mutate(kdm= case_when(Accession %in% kdm.vector ~ "KDM",
                                 TRUE ~ "ns"))

#MDAMB231

md<- big[,c(1,23,82,110)]
colnames(md)<- c("Accession", "Trigger", "No.Trigger", "kdm")

md_graph<- ggplot(md, aes(x=log10(Trigger), y=log10(No.Trigger))) +
  geom_point( aes(color = kdm, size = kdm, alpha=kdm)) +
  geom_smooth(method=lm , color="#0d97ca", fill="#0d97ca", se=TRUE) +
  theme_bw()+
  labs(title = "MDAMB231 average protein abundance")+
  stat_cor(method = "pearson")+
  scale_color_manual(values = c("#0d97ca","#696969"))+
  scale_size_manual(values = c(3,1))+
  scale_alpha_manual(values=c(1,0.2))+
  ylim(0,6)+
  xlim(0,6)


#HCC1806
hcc<- big[,c(1,19,69,110)]
colnames(hcc)<- c("Accession", "Trigger", "No.Trigger", "kdm")

hcc_graph<- ggplot(hcc, aes(x=log10(Trigger), y=log10(No.Trigger))) +
  geom_point( aes(color = kdm, size = kdm, alpha=kdm)) +
  geom_smooth(method=lm , color="#0d97ca", fill="#0d97ca", se=TRUE) +
  theme_bw()+
  labs(title = "HCC1806 average protein abundance")+
  stat_cor(method = "pearson")+
  scale_color_manual(values = c("#0d97ca","#696969"))+
  scale_size_manual(values = c(3,1))+
  scale_alpha_manual(values=c(1,0.2))+
  ylim(0,6)+
  xlim(0,6)


#MCF7
mcf7<- big[,c(1,21,75,110)]
colnames(mcf7)<- c("Accession", "Trigger", "No.Trigger", "kdm")

mcf7_graph<- ggplot(mcf7, aes(x=log10(Trigger), y=log10(No.Trigger))) +
  geom_point( aes(color = kdm, size = kdm, alpha=kdm)) +
  geom_smooth(method=lm , color="#0d97ca", fill="#0d97ca", se=TRUE) +
  theme_bw()+
  labs(title = "MCF7 average protein abundance")+
  stat_cor(method = "pearson")+
  scale_color_manual(values = c("#0d97ca","#696969"))+
  scale_size_manual(values = c(3,1))+
  scale_alpha_manual(values=c(1,0.2))+
  ylim(0,6)+
  xlim(0,6)


#MCF10A
mcf10a<- big[,c(1,25,87,110)]
colnames(mcf10a)<- c("Accession", "Trigger", "No.Trigger", "kdm")

mcf10a_graph<- ggplot(mcf10a, aes(x=log10(Trigger), y=log10(No.Trigger))) +
  geom_point( aes(color = kdm, size = kdm, alpha=kdm)) +
  geom_smooth(method=lm , color="#0d97ca", fill="#0d97ca", se=TRUE) +
  theme_bw()+
  labs(title = "MCF10A average protein abundance")+
  stat_cor(method = "pearson")+
  scale_color_manual(values = c("#0d97ca","#696969"))+
  scale_size_manual(values = c(3,1))+
  scale_alpha_manual(values=c(1,0.2))+
  ylim(0,6)+
  xlim(0,6)

figure_1<- ggarrange(md_graph, hcc_graph, mcf7_graph,mcf10a_graph,
                   ncol = 2,nrow = 2)

figure_1

#ggsave("Trigger channel_pearson correlation_proteome.png", figure_1, device = "png", width = 12, height = 12)
#ggsave("Trigger channel_pearson correlation_proteome.svg", figure_1, device = "svg", width = 12, height = 12)


```

## Principal component analysis

### No Trigger Channel
####prepare data frame to do a pca analysis
```{r}

bc_mat<- bc_df[,c(1:17)]

bc_mat<- bc_mat[!duplicated(bc_mat$Accession),]

rownames(bc_mat)<- bc_mat[,1]

bc_mat<- bc_mat[,-c(1)]

cols.num<- colnames(bc_mat)

bc_mat[cols.num]<- sapply(bc_mat[cols.num], as.numeric)

bc_mat<- na.omit(bc_mat)

bc_mat_t<- t(bc_mat)

bc_pca<- prcomp(bc_mat_t)

plot(bc_pca$x[,1], bc_pca$x[,2])

```
#### making a scree plot
```{r}
bc.pca.var<- bc_pca$sdev^2

bc.pca.var<- round(bc.pca.var/sum(bc.pca.var)*100,1)

barplot(bc.pca.var, main="Scree Plot", xlab="Principal Component", ylab="Percent Variation")

```

#### Using ggplot to make a nice pca plot
```{r}
bc.pca_data<- data.frame(sample= rownames(bc_pca$x),
                         x=bc_pca$x[,1],
                         y = bc_pca$x[,2])

bc.pca_data$cell<-c(rep("HCC1806",4) , 
                      rep("MCF10A",4),
                      rep("MCF7", 4),
                      rep ("MDAMB231",4))


```
##### PC1 vs PC2
```{r}

a<-ggplot(data=bc.pca_data,aes(label=sample,x=x,y=y, color = cell)) + 
 
  ggtitle("Proteome PCA Plot of Breast Cancer Cell Lines") +

  geom_point(aes( size = 4)) +
  
  scale_color_manual(values = c("MDAMB231"= "#3ca60e", "MCF10A"="#cc0000", "MCF7"="#26b3ff","HCC1806"="#674ea7"))+

  xlab(paste("PC1: ",bc.pca.var[1],"%",sep="")) +

  ylab(paste("PC2: ",bc.pca.var[2],"%",sep=""))+
   geom_mark_ellipse(aes(color = as.factor(cell)), expand = unit(2, "mm"), show.legend = F )+
  theme_classic()+
  theme(legend.text = element_text(size = 10))+
  guides(color=guide_legend(override.aes = list(size = 5)),
         shape = guide_legend(override.aes = list(size=5)))
 
a

#ggsave("bc_PCA PC1.eps", a, device= "eps", width = 6, height = 3)
```
#### looking at what contributes the most to PC1
```{r}

#getting the loading scores

loadingScores<- bc_pca$rotation[,1]

#getting the magnitudes of loading scores

geneScores<- abs(loadingScores)

#soring from high to low

geneScoreRanked<- sort(geneScores, decreasing = T)

#getting top 5 format 3

top5genes<- names(geneScoreRanked[1:10])

top_bc_pca<-bc_pca$rotation[top5genes,1]
top_bc_pca

```

### Trigger Channel

```{r}
#Protein

trig_mat<- trigger_df[,c(1:17)]

trig_mat<- trig_mat[!duplicated(trig_mat$Accession),]

rownames(trig_mat)<- trig_mat[,1]

trig_mat<- trig_mat[,-c(1)]

cols.num<- colnames(trig_mat)

trig_mat[cols.num]<- sapply(trig_mat[cols.num], as.numeric)

trig_mat<- na.omit(trig_mat)

trig_mat_t<- t(trig_mat)

trig_pca<- prcomp(trig_mat_t)

```


#### Plotting the pca
```{r}

plot(trig_pca$x[,1], trig_pca$x[,2])

```
making a scree plot
```{r}
trig.pca.var<- trig_pca$sdev^2

trig.pca.var<- round(trig.pca.var/sum(trig.pca.var)*100,1)

barplot(trig.pca.var, main="Scree Plot", xlab="Principal Component", ylab="Percent Variation")

```

Using ggplot to make a nice pca plot
```{r}
trig.pca_data<- data.frame(sample= rownames(trig_pca$x),
                         x=trig_pca$x[,1],
                         y = trig_pca$x[,2])

trig.pca_data$cell<-c(rep("HCC1806",4) , 
                      rep("MCF10A",4),
                      rep("MCF7", 4),
                      rep ("MDAMB231",4))


```
#PC1 vs PC2
```{r}

a<-ggplot(data=trig.pca_data,aes(label=sample,x=x,y=y, color = cell)) + 
 
  ggtitle("Proteome PCA Plot of Breast Cancer Cell Lines with the Trigger Channel") +

  geom_point(aes( size = 4)) +
  
  scale_color_manual(values = c("MDAMB231"= "#3ca60e", "MCF10A"="#cc0000", "MCF7"="#26b3ff","HCC1806"="#674ea7"))+

  xlab(paste("PC1: ",bc.pca.var[1],"%",sep="")) +

  ylab(paste("PC2: ",bc.pca.var[2],"%",sep=""))+
   geom_mark_ellipse(aes(color = as.factor(cell)), expand = unit(2, "mm"), show.legend = F )+
  theme_classic()+
  theme(legend.text = element_text(size = 10))+
  guides(color=guide_legend(override.aes = list(size = 5)),
         shape = guide_legend(override.aes = list(size=5)))
 
a

#ggsave("bc_PCA PC1 Trigger.eps", a, device= "eps", width = 6, height = 3)
```
looking at what contributes the most to PC1
```{r}

#getting the loading scores

loadingScores<- bc_pca$rotation[,1]

#getting the magnitudes of loading scores

geneScores<- abs(loadingScores)

#soring from high to low

geneScoreRanked<- sort(geneScores, decreasing = T)

#getting top 5 format 3

top5genes<- names(geneScoreRanked[1:10])

top_bc_pca<-trig_pca$rotation[top5genes,1]
top_bc_pca

```


# KDM comparison
## Number of PSMs and peptides between the two datasets (detected level)

```{r Detected level, no filtering}
#First pass
bc.kdm<-bc_protein %>%
  filter(Accession %in% kdm.vector)
bc.kdm<- inner_join( bc.kdm, gene_kdm, by = "Accession")
bc.kdm$type<- "No.Trigger"
bc.kdm_a<- bc.kdm[,c(4,6,7,34,53,70,71)]


#Trigger Channel
bc.kdm.trig<-trigger_protein %>%
  filter(Accession %in% kdm.vector)
bc.kdm.trig<- inner_join( bc.kdm.trig, gene_kdm, by = "Accession")
bc.kdm.trig$type<- "Trigger"
bc.kdm.trig_a<- bc.kdm.trig[,c(4,6,7,34,53,70,71)]


#Combining them
df<- rbind(bc.kdm_a, bc.kdm.trig_a)

#Plots

cols <- c("No.Trigger" = "black", "Trigger" = "#6A97A8") 

a<- ggplot(df, aes(x = Gene.Name, y = Coverage...., fill = type))+
  geom_bar(stat = "identity", color= "black", position = position_dodge2(preserve = "single"))+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust= 1))+
  labs(title = "% Peptide Coverage of KDM",
       y = "% Coverage",
       x = "KDM")+                                
  geom_text(aes(Gene.Name, label = Coverage....),
            position = position_dodge(width = 1),vjust=-0.25)+
  scale_fill_manual(values = cols)


b<- ggplot(df, aes(x = Gene.Name, y = X..PSMs, fill = type))+
  geom_bar(stat = "identity", color= "black",position = position_dodge2(preserve = "single"))+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust= 1))+
  labs(title = "# of PSMs for each KDM",
       y = "# of PSMs",
       x = "KDM")+                                
  geom_text(aes(Gene.Name, label = X..PSMs),
            position = position_dodge(width = 1),vjust=-0.25)+
  scale_fill_manual(values = cols)


c<- ggplot(df, aes(x = Gene.Name, X..Peptides, y = X..Peptides, fill = type))+
  geom_bar(stat = "identity", color= "black",position = position_dodge2(preserve = "single"))+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust= 1))+
  labs(title = "# of Peptides for each KDM",
       y = "# of Peptides",
       x = "KDM")+                                
  geom_text(aes(Gene.Name, label = X..Peptides),
            position = position_dodge(width = 1),vjust=-0.25)+
  scale_fill_manual(values = cols)


figure<- ggarrange(a, b, c,
                   ncol = 2,nrow = 2)

figure

#ggsave("Trigger channel stats ALL DETECTED.png", figure, device = "png", width = 20, height = 9)
#ggsave("Trigger channel stats ALL DETECTED.eps", figure, device = "eps", width = 20, height = 9)

```

## Filtering with Quant levels aka na omit filtered stuff
```{r}
#First pass
bc_protein<-bc_protein%>%
  filter(X..Unique.Peptides >1)
bc_protein<- bc_protein%>%
  filter(Protein.FDR.Confidence..Combined =="High")
bc.kdm<-bc_protein %>%
  filter(Accession %in% kdm.vector)
bc.kdm<- na.omit(bc.kdm)
bc.kdm<- inner_join( bc.kdm, gene_kdm, by = "Accession")
bc.kdm$type<- "No.Trigger"
#Subsetting: Accession, Peptide #, PSM number, # of unique peptides, Coverage, Gene.Name, and type
bc.kdm_a<- bc.kdm[,c(4,6,7,34,53,70,71)]


#Trigger Channel
trigger_protein<-trigger_protein%>%
  filter(X..Unique.Peptides >1)
trigger_protein<- trigger_protein%>%
  filter(Protein.FDR.Confidence..Combined =="High")
trigger.kdm<-trigger_protein %>%
  filter(Accession %in% kdm.vector)
trigger.kdm<- na.omit(trigger.kdm)
trigger.kdm<- inner_join( trigger.kdm, gene_kdm, by = "Accession")
trigger.kdm$type<- "Trigger"
#Subsetting: Accession, Peptide #, PSM number, # of unique peptides, Coverage, Gene.Name, and type
trigger.kdm_a<- trigger.kdm[,c(4,6,7,34,53,70,71)]


#Combining them
df<- rbind(bc.kdm_a, bc.kdm.trig_a)

#Plots

cols <- c("No.Trigger" = "black", "Trigger" = "#6A97A8") 

a<- ggplot(df, aes(x = Gene.Name, y = Coverage...., fill = type))+
  geom_bar(stat = "identity", color= "black", position = position_dodge2(preserve = "single"))+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust= 1))+
  labs(title = "% Peptide Coverage of KDM",
       y = "% Coverage",
       x = "KDM")+                                
  geom_text(aes(Gene.Name, label = Coverage....),
            position = position_dodge(width = 1),vjust=-0.25)+
  scale_fill_manual(values = cols)


b<- ggplot(df, aes(x = Gene.Name, y = X..PSMs, fill = type))+
  geom_bar(stat = "identity", color= "black",position = position_dodge2(preserve = "single"))+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust= 1))+
  labs(title = "# of PSMs for each KDM",
       y = "# of PSMs",
       x = "KDM")+                                
  geom_text(aes(Gene.Name, label = X..PSMs),
            position = position_dodge(width = 1),vjust=-0.25)+
  scale_fill_manual(values = cols)


c<- ggplot(df, aes(x = Gene.Name, X..Peptides, y = X..Peptides, fill = type))+
  geom_bar(stat = "identity", color= "black",position = position_dodge2(preserve = "single"))+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust= 1))+
  labs(title = "# of Peptides for each KDM",
       y = "# of Peptides",
       x = "KDM")+                                
  geom_text(aes(Gene.Name, label = X..Peptides),
            position = position_dodge(width = 1),vjust=-0.25)+
  scale_fill_manual(values = cols)


figure<- ggarrange(a, b, c,
                   ncol = 2,nrow = 2)

figure

#ggsave("Trigger channel stats Quantified.png", figure, device = "png", width = 20, height = 9)
#ggsave("Trigger channel stats Quantified.eps", figure, device = "eps", width = 20, height = 9)
```


## Investigating the PSMs of KDMs found in both datasets

```{r opening up psms}
no.trigger<- read.csv("/home/cberry/Documents/BC_TMT Analysis/psms.csv")

trigger<- read.csv("/home/cberry/Documents/BC_TMT Analysis/2024_01_08_ExplorisFAIMSaurora_CornettwithTrigger2.psm.csv")

library(dplyr)
```

### Pulling out KDM1A peptides
```{r}
no.trigger.1a<- no.trigger %>% filter(Master.Protein.Accessions == "O60341") #24 psms
trigger.1a<- trigger %>% filter(Master.Protein.Accessions == "O60341")#27 psms

# getting rid of duplicated peptides

no.trigger.1a.uni<- no.trigger.1a[!duplicated(no.trigger.1a$Annotated.Sequence),]#13 psms
trigger.1a.uni<- trigger.1a[!duplicated(trigger.1a$Annotated.Sequence),]#12 psms

common_psm<- intersect(no.trigger.1a.uni$Annotated.Sequence, trigger.1a.uni$Annotated.Sequence) #5 are in common [1] "[K].lQELEANPPSDVYLSSR.[D]" "[K].cDAVLcTLPLGVLk.[Q]"    "[K].tQEELkELLNk.[M]"      
#[4] "[K].eYDELAETQGk.[L]"       "[R].vHSYLER.[H]" 

#In no.trigger.1a.uni, K].cDAVLcTLPLGVLk.[Q] is seen 3 times, [K].lQELEANPPSDVYLSSR.[D] is seen 1 time, "[K].tQEELkELLNk.[M]" is seen 3 times, "[K].eYDELAETQGk.[L]" 1 time, "[R].vHSYLER.[H]"  2 times.
#9/24 psms from 5 sequences were in common

#in trigger.1a, [K].cDAVLcTLPLGVLk.[Q] 1 time, [K].lQELEANPPSDVYLSSR.[D] 3 time, [K].tQEELkELLNk.[M] 4 times, [K].eYDELAETQGk.[L] 2 times, [R].vHSYLER.[H] 2 times. 
#12/27 psms from 5 sequences were in common. [K].tQEELkELLNk.[M] was specifically seen a decent amount


```

### Looking at KDM3B
```{r}
no.trigger.3b<- no.trigger %>% filter(Master.Protein.Accessions == "Q7LBC6") #5 psms
trigger.3b<- trigger %>% filter(Master.Protein.Accessions == "Q7LBC6")#6 psms

# getting rid of duplicated peptides

no.trigger.3b.uni<- no.trigger.3b[!duplicated(no.trigger.3b$Annotated.Sequence),]#5 psms
trigger.3b.uni<- trigger.3b[!duplicated(trigger.3b$Annotated.Sequence),]#6 psms

common_psm<- intersect(no.trigger.3b.uni$Annotated.Sequence, trigger.3b.uni$Annotated.Sequence)
#Just the one"[K].sELWkPEAFSQEFGDQDVDLVNcR.[N]

# since there are no duplicates, the then it's 1/5 without the trigger and 1/6 with the trigger

```

### Looking at KDM5B
```{r}
no.trigger.5b<- no.trigger %>% filter(Master.Protein.Accessions == "Q9UGL1") #3 psms
trigger.5b<- trigger %>% filter(Master.Protein.Accessions == "Q9UGL1")#2 psms

# getting rid of duplicated peptides

no.trigger.5b.uni<- no.trigger.5b[!duplicated(no.trigger.5b$Annotated.Sequence),]#3 psms
trigger.5b.uni<- trigger.5b[!duplicated(trigger.5b$Annotated.Sequence),]#2 psms

common_psm<- intersect(no.trigger.5b.uni$Annotated.Sequence, trigger.5b.uni$Annotated.Sequence)
#None in common

```

# Now just looking at the other 4 KDMs seen in common, even thought the psm count is very different
## JMJD6, KDM2A, MINA, NO66. (RIOX2, RIOX1)

### JMJD6
```{r}
no.trigger.d6<- no.trigger %>% filter(Master.Protein.Accessions == "Q6NYC1") #10 psms
trigger.d6<- trigger %>% filter(Master.Protein.Accessions == "Q6NYC1")#30 psms

# getting rid of duplicated peptides

no.trigger.d6.uni<- no.trigger.d6[!duplicated(no.trigger.d6$Annotated.Sequence),]#6 psms
trigger.d6.uni<- trigger.d6[!duplicated(trigger.d6$Annotated.Sequence),]#8 psms

common_psm<- intersect(no.trigger.d6.uni$Annotated.Sequence, trigger.d6.uni$Annotated.Sequence)
#3 in common. "[R].dEGGNQQDEAITWFNVIYPR.[T]"    "[K].fFTDDLFQYAGEk.[R]"           "[K].vTRDEGGNQQDEAITWFNVIYPR.[T]"

#no trigger channel."[R].dEGGNQQDEAITWFNVIYPR.[T]" 2 times. [K].fFTDDLFQYAGEk.[R] 3 times. [K].vTRDEGGNQQDEAITWFNVIYPR.[T]. 1 time

#With trigger channel "[R].dEGGNQQDEAITWFNVIYPR.[T]" is seen 6 times, "[K].fFTDDLFQYAGEk.[R]"  is seen 7 times, and "[K].vTRDEGGNQQDEAITWFNVIYPR.[T]" is seen 8 times.

#These are high flying peptides

```


### KDM2A
```{r}
no.trigger.2a<- no.trigger %>% filter(Master.Protein.Accessions == "Q9Y2K7") #3 psms
dim(no.trigger.2a)
trigger.2a<- trigger %>% filter(Master.Protein.Accessions == "Q9Y2K7")#32 psms
dim(trigger.2a)
# getting rid of duplicated peptides

no.trigger.2a.uni<- no.trigger.2a[!duplicated(no.trigger.2a$Annotated.Sequence),]#3 psms
dim(no.trigger.2a.uni)
trigger.2a.uni<- trigger.2a[!duplicated(trigger.2a$Annotated.Sequence),]#16 psms
dim(trigger.2a.uni)

common_psm<- intersect(no.trigger.2a.uni$Annotated.Sequence, trigger.2a.uni$Annotated.Sequence)
#"[K].acVQGEcGVcHYcR.[D]" "[K].iLLEELANSDPk.[L]" 

#No trigger, each of these are seen once

#Without trigger, the first one is seen 1 time. ill is seen 3 times. Other peptides are more abundant

```

### MINA/RIOX2
```{r}
no.trigger.na<- no.trigger %>% filter(Master.Protein.Accessions == "Q8IUF8") #3 psms
dim(no.trigger.na)
trigger.na<- trigger %>% filter(Master.Protein.Accessions == "Q8IUF8")#43 psms
dim(trigger.na)
# getting rid of duplicated peptides

no.trigger.na.uni<- no.trigger.na[!duplicated(no.trigger.na$Annotated.Sequence),]#3 psms
dim(no.trigger.na.uni)
trigger.na.uni<- trigger.na[!duplicated(trigger.na$Annotated.Sequence),]#13 psms
dim(trigger.na.uni)

common_psm<- intersect(no.trigger.na.uni$Annotated.Sequence, trigger.na.uni$Annotated.Sequence)
#"[K].rATIQFHQPQR.[F]" "[R].eYSVEAEER.[I]"  

#No trigger, each one is seen once

#with trigger, [K].rATIQFHQPQR.[F] is seen 2 times, and [R].eYSVEAEER.[I] is seen 14 times. That one is a good flier

```

### NO66/RIOX1
```{r}
no.trigger.66<- no.trigger %>% filter(Master.Protein.Accessions == "Q9H6W3") #6 psms
dim(no.trigger.66)
trigger.66<- trigger %>% filter(Master.Protein.Accessions == "Q9H6W3")#17 psms
dim(trigger.66)
# getting rid of duplicated peptides

no.trigger.66.uni<- no.trigger.66[!duplicated(no.trigger.66$Annotated.Sequence),]#3 psms
dim(no.trigger.na.uni)
trigger.66.uni<- trigger.66[!duplicated(trigger.66$Annotated.Sequence),]#7 psms
dim(trigger.66.uni)

common_psm<- intersect(no.trigger.66.uni$Annotated.Sequence, trigger.66.uni$Annotated.Sequence)
#"[R].ePYGHLGPAELLEASPAAR.[S]" "[R].lGHFAPVDAVADQR.[A]"      "[R].vYHLEEPk.[C]"  

#No trigger, each one is seen once

#with trigger,[R].ePYGHLGPAELLEASPAAR.[S is seen 3 times, "[R].vYHLEEPk.[C]"  is seen once, and [R].lGHFAPVDAVADQR.[A]"  is seen 3 times. Not the most abundant peptide though

```

