```{r}
#This script looks at the trigger channel proteome differential proteome and performs WGCNA. Makes heatmap and GO term enrichment.
```

```{r}
library(dplyr)
library(WGCNA)
library(pheatmap)
library(clusterProfiler)

trig_df<- read.csv("Input/Trigger_channel_prot_stats_combined reps.csv")
trig_df<- trig_df[,-c(1)]
```


# WGCNA of the differentially abundant proteins
## ANOVA Analysis
```{r}
trig_df_2<- na.omit(trig_df)

trig_df_2<- trig_df_2[,c(1:17)]

trig_df_2<- as.data.frame(t(trig_df_2))

colnames(trig_df_2)<- trig_df_2[1,]
trig_df_2<- trig_df_2[-c(1),]

trig_df_2$type<- rownames(trig_df_2)

trig_df_2<- trig_df_2[,c(4312,1:4311)]

trig_df_2$type<- gsub("\\_.*","", trig_df_2$type)

n<- vector()

anova_run<- apply(trig_df_2[,2:ncol(trig_df_2)],2, function(a){

x<- aov(a~type, data = trig_df_2)
summary(x)
y<- summary(x)[[1]][["Pr(>F)"]][[1]]
n<- append(n,y)

return(n)})

trig_df_2<- as.data.frame(t(trig_df_2))

trig_df_2<- trig_df_2[-c(1),]

trig_df_2$anova_pvalue<- anova_run

```
# Significant Proteins

```{r}
protein.sig<- trig_df_2%>% filter(anova_pvalue <=0.05)
protein.sig$Accession<- rownames(protein.sig)

clean_sig<- protein.sig[,c(1:16, 18)]
rownames(clean_sig)<- clean_sig[,c(17)]
clean_sig<- clean_sig[,-c(17)]

# Take a quick look at what is in the data set:
dim(clean_sig)
names(clean_sig)

```
## Read in Trait info
```{r}

datTraits<- read.csv("Input/traits.csv")
rownames(datTraits)=datTraits[,1];datTraits=datTraits[,-1]
dim(datTraits);names(datTraits)

```
## Choosing the Soft Threshold
```{r}

clean_sig<- clean_sig %>% mutate_if(is.character, as.numeric)
clean_sig<- as.data.frame(t(clean_sig))
# Choose a set of soft-thresholding powers
powers = c(c(1:10), seq(from = 12, to=30, by=2))
# Call the network topology analysis function
sft = pickSoftThreshold(clean_sig, powerVector = powers, verbose = 5, networkType = "signed")
# Plot the results:
svg("Soft power Sig proteins.svg",10,5)
# sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit R^2",type="n",
     main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.85,col="red")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
     xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
     main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
dev.off()
```

## WGCNA Construction
```{r}
softPower = 20;
net = blockwiseModules(clean_sig, power = softPower, networkType = "signed",
                       TOMType = "signed", minModuleSize = 30,
                       reassignThreshold = 0, mergeCutHeight = 0.25,
                       numericLabels = TRUE, pamRespectsDendro = FALSE,
                       saveTOMs = TRUE,
                       saveTOMFileBase = "Example-1 ProDataTOM", 
                       verbose = 3)
table(net$colors)


# open a graphics window
svg("Protein Color modules Sig protein.svg",12,9)
#sizeGrWindow(12, 9)
# Convert labels to colors for plotting
mergedColors = labels2colors(net$colors)
# Plot the dendrogram and the module colors underneath
plotDendroAndColors(net$dendrograms[[1]], mergedColors[net$blockGenes[[1]]],
                    "Module colors",
                    dendroLabels = FALSE, hang = 0.03,
                    addGuide = TRUE, guideHang = 0.05)
dev.off()	
```
## Modules analysis and protein significant calculations
```{r}
moduleLabels = net$colors
moduleColors = labels2colors(net$colors)
MEs = net$MEs;
geneTree = net$dendrograms[[1]];

# Define numbers of genes and samples
nGenes = ncol(clean_sig);
nSamples = nrow(clean_sig);
# Recalculate MEs with color labels
MEs0 = moduleEigengenes(clean_sig, moduleColors)$eigengenes
MEs = orderMEs(MEs0)
moduleTraitCor = cor(MEs, datTraits, use = "p");
moduleTraitPvalue = corPvalueStudent(moduleTraitCor, nSamples);
```

#Module-trait relationship
```{r}
# open a graphics window
svg("Module square sig protein site.svg",5,6)
# sizeGrWindow(10,6)
# Will display correlations and their p-values
textMatrix =  paste(signif(moduleTraitCor, 2), "\n(",
                    signif(moduleTraitPvalue, 1), ")", sep = "");
dim(textMatrix) = dim(moduleTraitCor)
par(mar = c(6, 8.5, 3, 3));
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = moduleTraitCor,
               xLabels = names(datTraits),
               yLabels = names(MEs),
               ySymbols = names(MEs),
               colorLabels = FALSE,
               colors = blueWhiteRed(50),
               textMatrix = textMatrix,
               setStdMargins = FALSE,
               cex.text = 0.5,
               zlim = c(-1,1),
               main = paste("Module-trait relationships"))
dev.off()


```

## Correlated eigenpeptides in modules associated with traits and WGCNA results output
```{r}

Cancer = as.data.frame(datTraits$Cancer);
names(Cancer) = "Cancer"
# names (colors) of the modules
modNames = substring(names(MEs), 3)

geneModuleMembership = as.data.frame(cor(clean_sig, MEs, use = "p"));
MMPvalue = as.data.frame(corPvalueStudent(as.matrix(geneModuleMembership), nSamples));
names(geneModuleMembership) = paste("MM", modNames, sep="");
names(MMPvalue) = paste("p.MM", modNames, sep="");
geneTraitSignificance = as.data.frame(cor(clean_sig, Cancer, use = "p"));
GSPvalue = as.data.frame(corPvalueStudent(as.matrix(geneTraitSignificance), nSamples));
names(geneTraitSignificance) = paste("GS.", names(Cancer), sep="");
names(GSPvalue) = paste("p.GS.", names(Cancer), sep="");


# Create the starting data frame
geneInfo0 = data.frame(Peptides = names(clean_sig),
                       moduleColor = moduleColors,
                       geneTraitSignificance,GSPvalue)
# Order modules by their significance for Cancer
modOrder = order(-abs(cor(MEs, Cancer, use = "p")));
# Add module membership information in the chosen order
for (mod in 1:ncol(geneModuleMembership))
{
  oldNames = names(geneInfo0)
  geneInfo0 = data.frame(geneInfo0, geneModuleMembership[, modOrder[mod]], 
                         MMPvalue[, modOrder[mod]]);
  names(geneInfo0) = c(oldNames, paste("MM.", modNames[modOrder[mod]], sep=""),
                       paste("p.MM.", modNames[modOrder[mod]], sep=""))
}

geneInfo0<- na.omit(geneInfo0)
# Order the genes in the geneInfo variable first by module color, then by geneTraitSignificance
geneOrder = order(geneInfo0$moduleColor, -abs(geneInfo0$GS.Cancer));
geneInfo_sig = geneInfo0[geneOrder, ]
#save WGCNA results
#write.csv(geneInfo_sig, file = "WGCNA result_sig protein.csv", row.names = FALSE)

```


# Separating out modules for STRING and GO term analysis

```{r}
library(clusterProfiler)
library(org.Hs.eg.db)
library(dplyr)
library(ggplot2)
library(stringr)
all_protein<- read.csv("Input/No Trigger_channel_prot_stats.csv")
geneInfo_sig<- read.csv("Input/WGCNA result_sig protein.csv")

```

# Overall GO term analysis
```{r running function and analysis}

go_enrich<- function(a,x){

df<- a%>%
  filter(moduleColor == x)
  
gene<- df$Peptides
 
genes<-mapIds(org.Hs.eg.db, gene, "ENTREZID", "UNIPROT")

print("done mapping")

genes<- na.omit(genes)

print("Ready to enrich")

#Go to enrich
genes<- genes[!duplicated(genes)]

go_enriched<- enrichGO(genes,OrgDb = "org.Hs.eg.db", ont="all", universe =protein_bc_go)
go_enriched_2 <- simplify(go_enriched, cutoff=0.7, by="p.adjust", select_fun=min)
print("Enriched")
go_enriched_df<- as.data.frame(go_enriched)
a<- deparse(substitute(a))
write.csv(go_enriched_df, paste0(a, "_",x, "GO_terms.csv"))
print("Wrote file")
#Visualizing
go_enriched_dot<-dotplot(go_enriched, split="ONTOLOGY", showCategory = 5)+
  facet_grid(ONTOLOGY~., scale="free")+
  scale_fill_continuous(limits=c(0,0.05))+ 
  scale_y_discrete(labels=function(x) str_wrap(x, width=47))
  
ggsave(go_enriched_dot, file= paste0(a,"_",x,"GO_terms.eps"), device = "eps", width = 7, height = 7)
print("Wrote plot")


return(go_enriched_df)
}
```

## Running the GO enriched function

```{r}

#Make protein_bc_go aka background
gene<- all_protein$Peptide
 
genes<-mapIds(org.Hs.eg.db, gene, "ENTREZID", "UNIPROT")

protein_bc_go<- as.vector(na.omit(genes))

#Significant protein

sig_purple<- go_enrich(geneInfo_sig, "purple")
  #No enrichemnt of GO terms
sig_turquoise<- go_enrich(geneInfo_sig, "turquoise")
#sig_red<- go_enrich(geneInfo_sig, "red")
sig_black<- go_enrich(geneInfo_sig, "black")
sig_yellow<- go_enrich(geneInfo_sig, "yellow")
sig_pink<- go_enrich(geneInfo_sig, "pink")
sig_blue<- go_enrich(geneInfo_sig, "blue")
sig_green<- go_enrich(geneInfo_sig, "green")
sig_brown<- go_enrich(geneInfo_sig, "brown")
#sig_magenta<- go_enrich(geneInfo_sig, "magenta")


```


# Heatmap of Sig proteins with z score
```{r}
cal_z_score <- function(x){
 (x - mean(x)) / sd(x)
}
sig_protein<- bc_df_t_2%>%
  filter(anova_pvalue< 0.05)

sig_protein_heat<- sig_protein[,c(1:16)]
sig_protein_heat[]<- lapply(sig_protein_heat, as.numeric)

sig_protein_heat_score <- t(apply(sig_protein_heat, 1, cal_z_score)) # apply (df)
sig_protein_heat_score <- na.omit(sig_protein_heat_score)
sig_protein_heat_score<-as.data.frame(t(sig_protein_heat_score))

paletteLength <- 100

myColor <- colorRampPalette(c("navy", "white", "darkred"))(paletteLength)
myBreaks <- c(seq(min(sig_protein_heat_score), 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(max(sig_protein_heat_score)/paletteLength, max(sig_protein_heat_score), length.out=floor(paletteLength/2)))

svg("Significant proteins z scored heatmap.svg", height = 10, width =40)

a<- pheatmap(sig_protein_heat_score,
             color = myColor,
             cellwidth = 1,
             cellheight = 30,
             fontsize_row = 20,
             fontsize = 20,
             main = "Z-score of significant proteins",
             border_color = NA,
             cluster_rows = T,
             cluster_cols = T,
             show_colnames = F,
             show_rownames = T)

dev.off()

a
```

## Adding in WGCNA and cell line annotations
```{r}
wgcna_annotation<- read.csv("/home/cberry/Documents/BC_TMT Analysis/WGCNA/Protein/WGCNA result_sig protein.csv")

wgcna_annotation<- wgcna_annotation[,c(1:2)]
colnames(wgcna_annotation)<- c("Accession", "Module.color")
wgcna.annotation.2<- as.data.frame(wgcna_annotation[,-c(1)])
rownames(wgcna.annotation.2)<- wgcna_annotation$Accession
colnames(wgcna.annotation.2)<- "Module.colors"


```

```{r}
cal_z_score <- function(x){
 (x - mean(x)) / sd(x)
}
sig_protein<- bc_df_t_2%>%
  filter(anova_pvalue< 0.05)

sig_protein_heat<- sig_protein[,c(1:16)]
sig_protein_heat[]<- lapply(sig_protein_heat, as.numeric)

sig_protein_heat_score <- t(apply(sig_protein_heat, 1, cal_z_score)) # apply (df)
sig_protein_heat_score <- na.omit(sig_protein_heat_score)
sig_protein_heat_score<-as.data.frame(t(sig_protein_heat_score))

#Cell annotation
cell_annotation<-data.frame(cells= rep(c("HCC1806", "MCF10A","MCF7","MDAMB231"), each = 4))
rownames(cell_annotation)<- rownames(sig_protein_heat_score)

```


```{r}
library(pheatmap)
paletteLength <- 100

myColor <- colorRampPalette(c("navy", "white", "darkred"))(paletteLength)
myBreaks <- c(seq(min(sig_protein_heat_score), 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(max(sig_protein_heat_score)/paletteLength, max(sig_protein_heat_score), length.out=floor(paletteLength/2)))

annotation_color<- list(Module.colors=c(black = "black",blue = "blue", brown = "brown", cyan = "cyan", green = "green",turquoise = "turquoise", grey = "grey",brown = "brown", magenta = "magenta",pink = "pink", purple = "purple", red = "red", yellow = "yellow", grey60 = "dark grey", greenyellow = "green yellow", lightcyan = "light cyan", midnightblue = "navy", tan= "tan", salmon= "salmon"),
                        cells= c(HCC1806 = "#674ea7",MCF10A="#cc0000",MCF7 = "#26b3ff", MDAMB231 = "#3ca603"))



svg("Significant proteins z scored heatmap with wgcna.svg", height = 12, width =40)

a<- pheatmap(sig_protein_heat_score,
             annotation_col= wgcna.annotation.2,
             annotation_colors = annotation_color,
             annotation_row = cell_annotation,
             color = myColor,
             cellwidth = 1,
             cellheight = 30,
             fontsize_row = 20,
             fontsize = 20,
             main = "Z-score of significant proteins",
             border_color = NA,
             cluster_rows = T,
             cluster_cols = T,
             show_colnames = F,
             show_rownames = F)

dev.off()

a
```
